---
title: "hBayesDM_check"
output: html_document
date: "2024-04-23"
editor_options: 
  chunk_output_type: console
---

hBayesDM check

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(rstan)
library(hBayesDM)
#setwd("C:/Users/djpet/Documents/daw_resting_state")
#setwd("H:/Dan/rl_models")
setwd("/Volumes/Hera/Dan/rl_models")
#setwd("H:/Dan/rl_models/val")
par4 <- readRDS("ts_par4_7t_pet_results.rds")
par6 <- readRDS("ts_par6_7t_pet_results.rds")
par7 <- readRDS("ts_par7_7t_pet_results.rds")
```

Ok. This data is pretty intense. I'm going to subset out the parts I actually need to run locally. However, this needs to be done on Hera for computing reasons.

```{r}
#plot(par4, type = "trace")
#ggsave("par4_mustache.png")
#plot(par6, type = "trace")
#ggsave("par6_mustache.png")
#plot(par7, type = "trace")
#ggsave("par7_mustache.png")

#For Supp in Daw manuscript
plot(par7, type = "trace")
ggsave("par7_mustache_pi.png")
plot(par7)
ggsave("par7_postdist_pi.png")
plot(par7, type = "simple")
```

```{r}
printFit(par4,par6,par7, ic = "both")
#Outputting fit statistics for viewing.
fit_par7 <- par7$fit
fit_check <- fit_par7@sim$samples

#rhat check. Looking for less that 1.04 (liberal) ir less than 1.01 (conservative)
rhat_check6 <- rhat(par6)
rhat_check7 <- rhat(par7)
```

Saving other plots for later.

```{r}
plot(par4)
ggsave("par4_dist.png")
plot(par6)
ggsave("par6_dist.png")
plot(par7)
ggsave("par7_dist.png")

#Run this if we need individual plots for whole sample...
plotInd(par7, "pi")
#ggsave()
#plotInd()
#ggsave()
#plotInd()
#ggsave()
par4$parVals$
```

Testing posterior predictive check example. This is with the par4 model.

```{r}
## dimension of x$parVals$y_pred
dim(par4$parVals$y_pred_step1)   # y_pred --> 12000 (MCMC samples) x 414 (subjects) x 200 (trials)

y_pred_mean = apply(par4$parVals$y_pred_step1, c(2,3), mean)  # average of 4000 MCMC samples

dim(y_pred_mean)  # y_pred_mean --> 414 (subjects) x 200 (trials)

numSubjs = dim(par4$allIndPars)[1]  # number of subjects

subjList = unique(par4$rawdata$subjID)  # list of subject IDs
maxT = max(table(par4$rawdata$subjID))  # maximum number of trials
true_y = array(NA, c(numSubjs, maxT)) # true data (`true_y`)

## true data for each subject
for (i in 1:numSubjs) {
  tmpID = subjList[i]
  tmpData = subset(par4$rawdata, subjID == tmpID)
  true_y[i, ] = tmpData$level1_choice  # only for data with a 'choice' column
}

## Subject #1
plot(true_y[1, ], type="l", xlab="Trial", ylab="Choice (0 or 1)", yaxt="n")
lines(y_pred_mean[1,], col="red", lty=2)
axis(side=2, at = c(0,1) )
legend("bottomleft", legend=c("True", "PPC"), col=c("black", "red"), lty=1:2)
```
Let's save output for the 7 parameter model that "won"

Most important file is the allIndPars dataframe. That has the data that I'd need for analyses.

parVals is a list of 1d files that contain the posterior samples of all the parameters. They also contain the hyper-group parameters if those ever become useful.

Actually, I might as well save all of them

```{r}
par4_indpars <- par4$allIndPars
write.csv(par4_indpars, file = "par4_indpars.csv", row.names = FALSE)
par6_indpars <- par6$allIndPars
write.csv(par6_indpars, file = "par6_indpars.csv", row.names = FALSE)
par7_indpars <- par7$allIndPars
write.csv(par7_indpars, file = "par7_indpars.csv", row.names = FALSE)
```

