---
title: "rt_analyses"
author: "Daniel Petrie"
date: "2024-10-10"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r Global}
library("ggplot2") #For plotting
library("GGally") #ggpairs()
library("tidyverse") #Wranglin
library("dplyr") #Wranglin
library("interactions")
library("lme4") #MLM
library("lmerTest") #p-vals
library("ggeffects") #For marginal/conditional effects plots
library("marginaleffects") #For hypothesis_test()
library("parameters") #Other useful marginal effects functions
library("gdata") #upperTriangle()
library("mgcv") #GAMM
library("ggpubr") #Combining plots
library("bmlm") #Centering made easy
library("neuroCombat") #Harminization
library("LNCDR") #waterfall plot, lunaize plots 
library("gratia") #mgcv companion package. Using draw among other funcs.
library("psych") #Descriptives
library("ggrain") #Raincloud plot
library("ggseg") #Brain images
library("ggseg3d") #3d brain images
library("see") #Theme modern
library("viridis") #Additional colors
library("viridisLite") #Additional colors
library("ggnewscale") #new_scale()
#library("corrplot") #Corrplot()
#Working directory (change to something better (onedrive?, something else?) at some point)
#Hera feels correct at this moment. All files could live in directory R for this project.
setwd("C:/Users/djpet/OneDrive/Documents/daw_resting_state/rt_analyses")

full <- read.csv("C:/Users/djpet/OneDrive/Documents/daw_resting_state/daw_project_081624.csv", 
                 header = TRUE)

rt <- read.csv("all_daw.csv", header = TRUE)
```


Cleaning RT data

```{r}
#Removing "from" column
luna_rt <- rt %>%
  select(-from)

#Removes rows where choice is not a number. RT files are concatenated such that each subject has a header row that needs to be removed.
luna_rt <- luna_rt[!grepl("[^0-9.]", luna_rt$choice1), ]

#Reordering row numbers
row.names(luna_rt) <- NULL

#Changes columns to numeric. All are reading in as character variables for some reason.
cols_to_convert <- c("choice1", "choice2", 
                     "state", "money", "rts1", "rts2")
luna_rt[cols_to_convert] <- lapply(luna_rt[cols_to_convert], as.numeric)


#Separating id column into "id" and "visit"
luna_rt <- luna_rt %>%
  separate(id, c("lunaid", "behave.date"))

#Adding trial number for indexing purposes
luna_rt <-  luna_rt %>% 
  group_by(lunaid, behave.date) %>%
  mutate(trial = row_number()) 

#Remove rows where behave data = NA. These are test subjects
luna_rt <- luna_rt %>%
  filter(!(lunaid %in% c(99999, "aqtest", "test")))

length(unique(luna_rt$lunaid)) #487 seems appropiate

#Visit number for lagged
luna_rt <- luna_rt %>% 
  group_by(lunaid) %>% 
  mutate(visitnum = as.integer(factor(behave.date, levels = unique(behave.date))))

#I think all I need is to create a (non) lagged column reflecting whether current trial was common vs. rare.
luna_rt <- luna_rt %>% 
  mutate(commonrare = as.factor(ifelse((choice1 == 1 & state == 2) |
                                  (choice1 == 2 & state == 3),
                                "Common",
                                "Rare")))



#Don't think I need lagged stuff for this analyses.
#Lagging variables to calculate transitional variables.
luna_rt <- luna_rt %>% 
  group_by(lunaid, visitnum) %>% 
  mutate(choice1lag = lag(choice1), #Indexing for common/rare transition
         choice2lag = lag(choice2), #Indexing for common/rare transition
         statelag = lag(state),     #Indexing for common/rare transition
         moneylag = lag(money),     #Indexing for reward on previous trial
         rts1lag = lag(rts1),       #Lagging RT stage 1 just in case  
         rts2lag = lag(rts2))       #Lagging RT stage 2 for after common vs rare transition

# transitional variables
luna_rt <- luna_rt %>% 
  mutate(commonrare_l = as.factor(ifelse((choice1lag == 1 & statelag == 2) | 
                                         (choice1lag == 2 & statelag == 3),
                                       'Common', 
                                       'Rare')), 
         commonraredummy_l = ifelse(commonrare_l=="Common", 
                                  1, 
                                  -1),
         commonraredummy = ifelse(commonrare == "Common",
                                  1,
                                  -1),
         moneylagdummy = ifelse(moneylag == 1, 
                                1, 
                                -1), 
         firststagestay = ifelse(choice1 == choice1lag, 
                                 1, 
                                 0), 
         stayswitchwinlose = ifelse(firststagestay==1 & moneylag==0, 'lose-stay',
                             ifelse(firststagestay==1 & moneylag==1, 'win-stay', 
                                    ifelse(firststagestay==0 & moneylag==0,
                                           'lose-switch', 
                                           'win-switch'))),
         winswitch = ifelse(stayswitchwinlose== "win-switch",
                            1,
                            0),
         winswitch_common = ifelse(commonrare == "Common" & 
                            stayswitchwinlose == "win-switch", 
                            1,
                            0),
          winswitch_rare = ifelse(commonrare == "Rare" &
                            stayswitchwinlose == "win-switch",
                          1,
                          0))
```


Cleaning full data for merging.

```{r}
full_sub <- full %>%
  select(id, visitnum, age, sex, study, behave.date, 
         modelbased, modelfree, firststagestay,
         modelbased_z, modelfree_z, firststagestay_z) %>%
  rename(lunaid = id)
```

Merging chunk and some preprocessing.

```{r}
dat <- merge(luna_rt, full_sub, by = c("lunaid", "visitnum"))

#Age groups for plotting
#Converting rt to milliseconds
#Z-scoring age and rt in milliseconds for analyses,
dat <- dat %>%
  mutate(age_cat = cut(age,
                       breaks = c(10,13,17,24,34),
                       labels = c("10-13 years", "14-17 years", "18-24 years", "25-34 years"),
                       include.lowest = TRUE),
         rts2_ms = rts2 * 1000,
         rts2_ms_z = scale(rts2_ms),
         age_z = scale(age)) %>%
  arrange(lunaid, visitnum, trial)
```



This script examines RT at the second stage choice as a function of transition type using a multilevel model. If subjects were not aware of transition structure, we would expect no response time differences after common transitions compared with rare transitions.

Eq:
RT_2nd stage ~ 1 + Age + Transition + Age:Transition + (1|id)

```{r}
t_1 <- lmer(rts2_ms ~ 1 + commonraredummy + age_z + 
              commonraredummy:age_z + (1|lunaid),
          data = dat,
          na.action = na.exclude)
summary(t_1)

t_2 <- lmer(rts2_ms ~ 1 + commonraredummy + age_z + 
              commonraredummy:age_z + (1 + commonraredummy|lunaid),
          data = dat,
          na.action = na.exclude)
summary(t_2)

t_3 <- lmer(rts2_ms ~ 1 + commonraredummy + age_z + 
            commonraredummy:age_z + (1|lunaid:visitnum),
          data = dat,
          na.action = na.exclude)
summary(t_3)
confint(t_3)
anova(t_1, t_2, t_3)
AIC(t_1, t_2, t_3)
BIC(t_1, t_2, t_3)

#t-3 seems to be the best model.
plot(ggpredict(t_3, terms = c("age_z", "commonraredummy")))
```

Plot RT by age group

```{r}
#Create new data frame by calculating mean, sd, N, and se from trial level data
rt_stats <- dat %>%
  group_by(lunaid, visitnum, age_cat, commonrare) %>%
  dplyr::summarize(mean_rt = mean(rts2_ms, na.rm = TRUE),
            sd_rt = sd(rts2_ms, na.rm = TRUE),
            N = n(),
            se_rt = (sd_rt/sqrt(N)))

# Plot second-stage RTs by age group 
rt_stats_group <- rt_stats %>%
  group_by(commonrare, age_cat) %>%
  dplyr::summarize(mean_rt_group = mean(mean_rt, na.rm = TRUE),
            N = n(),
            sd_rt_group = sd(mean_rt, na.rm = TRUE),
            se_rt = (sd_rt_group/sqrt(N)))
#Plot
rt_plot_group <- ggplot(rt_stats_group, 
                        aes(x = commonrare, 
                            y = mean_rt_group, 
                            fill = commonrare)) + 
  geom_bar(position = "dodge", 
           stat = "identity", 
           color = "black") + 
  geom_errorbar(aes(x = commonrare, 
                    ymin = mean_rt_group - se_rt, 
                    ymax = mean_rt_group + se_rt), 
                width = 0) +
  xlab("Previous Transition Type") +
  ylab("Response Time (sec)") +
  facet_wrap(~age_cat, nrow = 1) +
  coord_cartesian(ylim = c(500, 1000)) +
  scale_fill_manual(values = c("royalblue4", "firebrick2")) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
                panel.spacing.x = unit(1, "lines"),
                axis.line = element_line(size = .1),
                strip.text.x = element_text(size = 8),
                axis.title = element_text(size = 8),
                axis.text = element_text(size = 8),
                plot.title = element_text(size = 8, face = "bold"),
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))
rt_plot_group


ggsave(filename = 
         "C:/Users/djpet/OneDrive/Documents/daw_resting_state/figures/figure_S5/rt_plot_group.png", 
       plot = rt_plot_group,
       device = "png", 
       dpi = 500, 
       units = "mm",
       width = 90, 
       height = 60)
```


Decker and Nussembaum also tested something like this:

Model based coeffiecient ~ 1 + RT_difference + Age + RT_difference:Age + (1|id)

```{r}
#Calculate each subjects RT difference
rt_diff <- rt_stats %>%
  group_by(lunaid, visitnum, age_cat) %>%
  dplyr::summarize(rt_diff = mean(mean_rt[commonrare == "Rare"], na.rm = TRUE) -
                      mean(mean_rt[commonrare == "Common"], na.rm = TRUE)) %>%
  ungroup()

#Mergin modelbased and first stage stay
rt_diff_daw <- merge(rt_diff, full_sub, by = c("lunaid", "visitnum"))

#Re-zscore for analyses
rt_diff_daw <- rt_diff_daw %>%
  mutate(age_z = scale(age),
         rt_diff_z = scale(rt_diff))
```

Model

```{r}
q <- lmer(modelbased ~ 1 + age_z + rt_diff_z + age_z:rt_diff_z + (1|lunaid),
          data = rt_diff_daw)
summary(q)
confint(q)
plot(ggpredict(q, terms = c("rt_diff_z", "age_z[-2,-1,0,1,2]")))

plot(ggpredict(q, terms = c("age_z", "rt_diff_z[-2,-1,0,1,2]")))

rt_mb_plot <- ggplot(rt_diff_daw, aes(x = rt_diff, y = modelbased)) +
  geom_point(stat = "identity", size = 0.5) + 
  geom_smooth(method = "lm", color = "black", linewidth = 0.5) +
  facet_wrap(~age_cat, nrow = 1) +
  ylab("Reward x Transition Interaction Effect") +
  xlab("Response Time Difference (Rare - Common) (ms)") +
 # coord_cartesian(ylim = c(-.5, 1.5), xlim = c(-200, 600)) +
  theme_minimal() + 
  theme(panel.grid = element_blank(),
        panel.spacing.x = unit(1, "lines"),
        axis.line = element_line(size = .1),
        strip.text.x = element_text(size = 8),
        axis.title = element_text(size = 8),
        axis.text = element_text(size = 8),
        plot.title = element_text(size = 8, face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1))
rt_mb_plot

ggsave(filename = 
         "C:/Users/djpet/OneDrive/Documents/daw_resting_state/figures/figure_S5/rt_mb_plot.png", 
       plot = rt_mb_plot,
       device = "png", 
       dpi = 500, 
       units = "mm",
       width = 90, 
       height = 60)
```

