---
title: "check"
author: "Daniel Petrie"
date: "2024-08-15"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(psych)
library("magick")
library("cowplot")
library(gridExtra)
library(ggpubr)
library(lme4)
library(lmerTest)
#Working directory
setwd("C:/Users/djpet/Documents/daw_resting_state")

#Full data so I can extract the correct subjects
full <- read.csv("daw_project_070324.csv", header = TRUE)
#Trial level Daw data. I do not need to run the logistic regression models. I only need to run the first part of the cleaning code to calculate the probability of first stage stay on average (i think).
luna_7t <- read.csv("cleaning/luna_7tbrainmech.csv", header = TRUE)
luna_pet <- read.csv("cleaning/luna_pet.csv", header = TRUE)
```


Full cleaning.

```{r Full Cleaning}
#Creating a different sex variable for some plots/analyses
full <- full %>%
  mutate(sex = as.character(sex),
    sex_p = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female",
    TRUE ~ sex 
  ))

#Making visitnum a factor. Can change accordingly
full$visitnum <- as.factor(full$visitnum)

#Making sex a factor
full$sex <- as.factor(full$sex)

#Making an ordered factor.
full$sex_p <- ordered(full$sex_p, levels = (c("Male", "Female")))

#Inverse age for linear models.
full$inv_age <- 1/full$age

#Checking for duplicate rows due to weird merging situation I put myself in.
full[which(duplicated(full$modelbased)),c(1:3, 8, 20)] #11475_2/11498_2/11589_2 are duplicates.
#These ids have duplicated Daw visits, but different rest days. Taking rows with imaging data.

full <- full %>%
  filter(!(id == "11475" & visitnum == "2") & 
           !(id == "11498" & visitnum == "2") &
           !(id == "11589" & visitnum == "2"))

#Treating visitnum as numeric?
full$visitnum_numeric <- as.numeric(full$visitnum)
```

**Cleaning Daw Behavioral Data**

I am combining to run the logistic model. Then I will separate by study.

```{r Daw Cleaning}
#Separating id column into "id" and "visit"
luna_7t <- luna_7t %>%
  separate(id, c("id", "vdate"))

luna_pet <- luna_pet %>%
  separate(id, c("id", "vdate"))

#Adding trial number
luna_7t <- luna_7t %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

luna_pet <- luna_pet %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

#Removing id with identical data that was copied across studies.
luna_pet <- luna_pet %>% group_by(id) %>% filter(id != "11565")

#Adding scanner information. Ashley slack stated that Siemens for 7T, Siemens Biograph mMR PET/MRI for PET. Seems like they only need a binary code situation here, but I will fuss with that during the neuroCombat portion of the code. This will also be useful for seeing which study came from what subje t.
luna_7t$study <- "7t"
luna_pet$study <- "PET"

#Similar id's across data sets. Check to make sure it looks correct with visit_info data set.
same_ids <- intersect(luna_7t$id, luna_pet$id)
same_ids
#"10195" ok
#"10997" ok
#"11537" ok
#"11561" ok
#"11565" Not ok. Tested on same day. Fixed above!
#"11575" ok
#"11641" ok
#"11651"
#luna_7t %>% filter(id == "11651")
#luna_pet %>% filter(id == "11651")
#visit_info %>% filter(id == "11651")

#Combining data. ADD HABIT HERE
luna_all <- bind_rows(luna_7t, luna_pet)

# compute visit number
luna_all <- luna_all %>% 
  group_by(id) %>% 
  mutate(visitnum = as.integer(factor(vdate, levels = unique(vdate))))
```

Ok. Now I will mess around with the lagged portion of the code. I need to figure out how to code NA's correctly for 

```{r}
#Subsetting subject with multiple instances of not responding. There is also two visits to ensure coding is correct.
#luna_all_sub <- luna_all %>%
#  filter(id == "11537")

#Creating lagged variables. Add trial
luna_all <- luna_all %>% 
  group_by(id, visitnum) %>% 
  mutate(choice1lag = lag(choice1),
         choice2lag = lag(choice2),
         statelag = lag(state),
         moneylag = lag(money),
         visitnumlag = lag(visitnum))

# transitional vars...
luna_all <- luna_all %>% 
  mutate(commonrare = as.factor(ifelse((choice1lag == 1 & statelag == 2) |
                                         (choice1lag == 2 & statelag == 3),
                                       'Common',
                                       ifelse(choice1lag == 0 & statelag == 0, NA, 'Rare'))), 
         commonraredummy = ifelse(commonrare=="Common", 
                                  1, 
                                  -1), 
         moneylagdummy = ifelse(moneylag == 1, 
                                1,
                                ifelse(commonraredummy == "NA", NA, -1)), 
         firststagestay = ifelse(choice1 == choice1lag, 
                                 1,
                                 ifelse(commonraredummy == "NA", NA, 0)), 
         stayswitchwinlose = ifelse(firststagestay==1 & moneylag==0, 'lose-stay',
                             ifelse(firststagestay==1 & moneylag==1, 'win-stay', 
                                    ifelse(firststagestay==0 & moneylag==0,
                                           'lose-switch', 
                                           'win-switch'))))

#luna_all <- luna_all %>% mutate(winswitch = ifelse(stayswitchwinlose== "win-switch",
#                            1,
#                            0))
#luna_all <- luna_all %>% mutate(
#  winswitch_common = ifelse(commonrare == "Common" & 
#                            stayswitchwinlose == "win-switch", 
#                            1,
#                            0),
#  winswitch_rare = ifelse(commonrare == "Rare" &
#                            stayswitchwinlose == "win-switch",
#                          1,
#                          0))
```

Comparing model output.

Combining the data.

```{r Combining Data}
#Selecting columns of interest from full
full_sub <- full %>%
  dplyr::select(id, visitnum, age, study, sex, behave.date)

#Selecting columns of interest from Daw
#I think I will need firststagestay, moneylag, commonrate
luna_all_sub <- luna_all %>%
  dplyr::select(id, visitnum, vdate, trial, moneylag, moneylagdummy, commonrare, commonraredummy, firststagestay) %>%
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  rename(behave.date = vdate,
         visitnum_daw = visitnum)

#Remember to organize by Date. Idea is to make sure that they match up appropiately.
stay_prob <- merge(luna_all_sub, full_sub, by = c("id", "behave.date"))

#Adding dichotomous age
#stay_prob <- stay_prob %>%
#  mutate(age_cat = if_else(age < 18, 0, 1))
age_bins <- cut(stay_prob$age,
                breaks = c(10,13,17,24,34),
                labels = c("10-13 years", "14-17 years", "18-24 years", "25-34 years"),
                include.lowest = TRUE)
stay_prob <- stay_prob %>%
  mutate(age_cat = age_bins)
```


```{r}
intmodeltoplot <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=stay_prob,
                        na.action = na.exclude,
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot)
```

```{r}
#Extracting random effects
dawranefint <- ranef(intmodeltoplot)
head(dawranefint$`id:visitnum`)

#dawranefintws <- ranef(intmodeltoplotws)
#head(dawranefintws$`id:visitnum`)

#Extracting fixed effects
dawfixedeffectsint <- summary(intmodeltoplot)$coefficients
dawfixedeffectsint

#dawfixedeffectsintws <- summary(intmodeltoplotws)$coefficients
#dawfixedeffectsintws

#Creating dataframe consisting of MB/MF/Habit parameter.
dawsubjecterms <- data.frame(
  idtemp = row.names(dawranefint$`id:visitnum`), 
  modelbased = dawranefint$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint[4,1], 
  modelfree = dawranefint$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint[3,1],
  commonrare = dawranefint$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint[2,1],
  firststagestay = dawranefint$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint[1,1])
#,
#  winswitch = dawranefintws$`id:visitnum`$`(Intercept)` +
#    dawfixedeffectsintws[1,1])
  
#Create id column
dawsubjecterms$id <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                            ":"),'[',1))
#Create visitnum column
dawsubjecterms$visitnum <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                                  ":"),'[',2))
#Checking
head(dawsubjecterms)

# Selecting variable. Doing explicitly to reorder
dawsubjecterms <- dawsubjecterms %>% dplyr::select(id, visitnum, modelbased, 
                                         modelfree, commonrare, 
                                         firststagestay) 


luna_all <- luna_all %>% dplyr::select(id, visitnum, vdate, study) %>% distinct()


#Adding visit number number
#luna_all <- luna_all %>%
#  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
#  group_by(id) %>%
#  arrange(vdate) %>%
#  mutate(visitnum = dense_rank(vdate))

#Mergin date information with daw subject terms
dawsubjecterms <- merge(dawsubjecterms, luna_all, by = c("id", "visitnum"))

#Removing visitnum after merging
dawsubjecterms <- dawsubjecterms %>% 
  dplyr::select(!visitnum) %>% 
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  rename(behave.date = vdate)

#Subsetting age from full data
full_age <- full %>% select(id, visitnum, behave.date, age, harox_putamen_harm, sex)
test <- merge(dawsubjecterms, full_age, by = c("id", "behave.date"), all.x = TRUE)

#Redo visit numbers
test <- test %>% dplyr::select(!visitnum) %>%
  group_by(id) %>%
  arrange(behave.date) %>%
  mutate(visitnum = dense_rank(behave.date))
```

```{r}
ggplot(data = test, 
               aes(x=age, y=firststagestay, group = id)) + 
  geom_point(alpha = 0.7) +
  geom_line(alpha = 0.7) +
  stat_smooth(method = "lm", aes(group = 1))

#Treating visitnum as numeric?
test$visitnum_numeric <- as.numeric(test$visitnum)

#Treating id as factor for og gam fitting
test$id_fac <- as.factor(test$id)
test_5 <- gam(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = F) +
                 s(firststagestay, k = 3, fx = F) +
                 s(modelbased, k = 3, fx = F)+
                     s(id_fac, bs = "re"),
                     method = "REML",
                     data = test)
summary(test_5)
plot(ggpredict(test_5, terms = c("age", "firststagestay"))) + scale_y_continuous(transform = "reverse")
plot(ggpredict(test_5, terms = c("age", "modelbased"))) + scale_y_continuous(transform = "reverse")

test_6 <- gam(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = F) +
                 s(age, by = firststagestay, k = 3, fx = F) +
                 s(age, by = modelbased, k = 3, fx = F)+
                #s(age, by = modelfree, k = 3, fx = F) +
                     s(id_fac, bs = "re"),
                     method = "REML",
                     data = test)
summary(test_6)
plot(ggpredict(test_6, terms = c("age", "firststagestay"))) + scale_y_continuous(transform = "reverse")
plot(ggpredict(test_6, terms = c("age", "modelbased"))) + scale_y_continuous(transform = "reverse")
```


I'm also curious about missing values and whether that depended on a subjects age.

```{r}
full_age <- full %>% select(id, behave.date, age, sex)

luna_all_sub <- luna_all %>% 
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  rename(behave.date = vdate)

test <- merge(luna_all_sub, full_age, by = c("id", "behave.date"), all.x = TRUE)

# Summarize the data and calculate proportions. This is also useful to get a sense of missing responses.
summary_data <- test %>%
  group_by(id, visitnum) %>%
  summarise(count_choice1_0 = sum(choice1 == 0 | choice2 == 0))

#Adding ages
age_test <- summary_data %>%
  left_join(test %>% select(id,visitnum,age), by = c("id", "visitnum")) %>% distinct()

ggplot(age_test, aes(x = age, y = count_choice1_0)) +
  geom_point() +                     # Scatter plot
  geom_smooth(method = "lm", col = "blue") +  # Regression line
  labs(title = "Relationship between Age and Count of choice1 == 0",
       x = "Age",
       y = "Count of choice1 == 0") +
  theme_minimal()

summary(lm(count_choice1_0 ~ 1 + age, data = age_test))
```

It looks like there are no age-related trends in the number of missing trials during the task. In fact, most participants had very little missingness.





Another sanity check, would be to re-clean this data and simply remove all instances of no response. The idea would be that the next instance of responding should corospond to the actual last time they chose a rocketship. This would be a sensitivity check in case someone asks about it.

```{r}
table(luna_all$choice1)
table(luna_all$choice2)
1376-925 #925 trials where subject did not respond on stage 1. 451 trials where subjects did not respond on stage 2.

1376/83400 #1.6% of trials are missing.

#Removing trials where subjects did not respond.
83400-1376 #Looking for 82,024 trials

#Removing trials where choice 1 == 0 and choice 2 == 0.
luna_all <- luna_all %>%
  filter(!(choice1 == 0 | choice2 == 0))

#strating with luna all
#Creating lagged variables. Add trial
luna_all <- luna_all %>% 
  group_by(id, visitnum) %>% 
  mutate(choice1lag = lag(choice1),
         choice2lag = lag(choice2),
         statelag = lag(state),
         moneylag = lag(money),
         visitnumlag = lag(visitnum))

# transitional vars...
luna_all <- luna_all %>% 
  mutate(commonrare = as.factor(ifelse((choice1lag == 1 & statelag == 2) |
                                         (choice1lag == 2 & statelag == 3),
                                       'Common',
                                       'Rare')), 
         commonraredummy = ifelse(commonrare=="Common", 
                                  1, 
                                  -1), 
         moneylagdummy = ifelse(moneylag == 1, 
                                1,
                                -1), 
         firststagestay = ifelse(choice1 == choice1lag, 
                                 1,
                                 0), 
         stayswitchwinlose = ifelse(firststagestay==1 & moneylag==0, 'lose-stay',
                             ifelse(firststagestay==1 & moneylag==1, 'win-stay', 
                                    ifelse(firststagestay==0 & moneylag==0,
                                           'lose-switch', 
                                           'win-switch'))))

intmodeltoplot <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all,
                        na.action = na.exclude,
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot)
```


```{r}
#Extracting random effects
dawranefint <- ranef(intmodeltoplot)
head(dawranefint$`id:visitnum`)

#dawranefintws <- ranef(intmodeltoplotws)
#head(dawranefintws$`id:visitnum`)

#Extracting fixed effects
dawfixedeffectsint <- summary(intmodeltoplot)$coefficients
dawfixedeffectsint

#dawfixedeffectsintws <- summary(intmodeltoplotws)$coefficients
#dawfixedeffectsintws

#Creating dataframe consisting of MB/MF/Habit parameter.
dawsubjecterms <- data.frame(
  idtemp = row.names(dawranefint$`id:visitnum`), 
  modelbased = dawranefint$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint[4,1], 
  modelfree = dawranefint$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint[3,1],
  commonrare = dawranefint$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint[2,1],
  firststagestay = dawranefint$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint[1,1])
#,
#  winswitch = dawranefintws$`id:visitnum`$`(Intercept)` +
#    dawfixedeffectsintws[1,1])
  
#Create id column
dawsubjecterms$id <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                            ":"),'[',1))
#Create visitnum column
dawsubjecterms$visitnum <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                                  ":"),'[',2))
#Checking
head(dawsubjecterms)

# Selecting variable. Doing explicitly to reorder
dawsubjecterms <- dawsubjecterms %>% dplyr::select(id, visitnum, modelbased, 
                                         modelfree, commonrare, 
                                         firststagestay) 


luna_all <- luna_all %>% dplyr::select(id, visitnum, vdate, study) %>% distinct()


#Adding visit number number
#luna_all <- luna_all %>%
#  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
#  group_by(id) %>%
#  arrange(vdate) %>%
#  mutate(visitnum = dense_rank(vdate))

#Mergin date information with daw subject terms
dawsubjecterms <- merge(dawsubjecterms, luna_all, by = c("id", "visitnum"))

#Removing visitnum after merging
dawsubjecterms <- dawsubjecterms %>% 
  dplyr::select(!visitnum) %>% 
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  rename(behave.date = vdate)

#Subsetting age from full data
full_age <- full %>% select(id, visitnum, behave.date, age, harox_putamen_harm, sex)
test <- merge(dawsubjecterms, full_age, by = c("id", "behave.date"), all.x = TRUE)

#Redo visit numbers
test <- test %>% dplyr::select(!visitnum) %>%
  group_by(id) %>%
  arrange(behave.date) %>%
  mutate(visitnum = dense_rank(behave.date))
```

Ran plots above from this and looks similar enough. 1% missing is not a crazy amount.