---
title: "cic_test_script"
author: "Daniel Petrie"
date: "2024-07-02"
output: html_document
editor_options: 
  chunk_output_type: console
---

Preliminary script that checks whether cic atlas is worth pursuing.

1.) Clean cic data and take weighted mean across hemispheres.

2.) Merge with full data set (potentially subset variables of interest)

3.) Run the tv-parameter analyses across different regions.

4.) ???

5.) Profit?


```{r Global}
library(ggplot2)
library(ggridges)
library(tidyverse)
library(dplyr)
library(neuroCombat)
library(LNCDR)
library(ggrain)

setwd("C:/Users/djpet/Documents/daw_resting_state")
#tat2_7t <- read.delim("cleaning/7t_cic.tsv", header = TRUE)
#tat2_pet <- read.delim("cleaning/pet_cic.tsv", header = TRUE)
#merge_7t <- read.csv("cleaning/merged_7t.csv", header = TRUE)
#merge_pet <- read.csv("cleaning/merged_pet.csv", header = TRUE)
full <- read.csv("daw_project_060524.csv", header = TRUE)
tat2_7t <- read.delim("cleaning/7t_cic_vox.tsv", header = TRUE)
tat2_pet <- read.delim("cleaning/pet_cic_vox.tsv", header = TRUE)
```


**Cleaning full data**


```{r full Cleaning}
#Creating a different sex variable for some plots/analyses
full <- full %>%
  mutate(sex = as.character(sex),
    sex_p = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female",
    TRUE ~ sex 
  ))

#Making visitnum a factor. Can change accordingly
full$visitnum <- as.factor(full$visitnum)

#Making sex a factor
full$sex <- as.factor(full$sex)

#Making an ordered factor.
full$sex_p <- ordered(full$sex_p, levels = (c("Male", "Female")))

#Inverse age for linear models.
full$inv_age <- 1/full$age

#Checking for duplicate rows due to weird merging situation I put myself in.
full[which(duplicated(full$modelbased)),c(1:3, 8, 20)] #11475_2/11498_2/11589_2 are duplicates.
#These ids have duplicated Daw visits, but different rest days. Taking rows with imaging data.

full <- full %>%
  filter(!(id == "11475" & visitnum == "2") & 
           !(id == "11498" & visitnum == "2") &
           !(id == "11589" & visitnum == "2"))

#Treating visitnum as numeric?
full$visitnum_numeric <- as.numeric(full$visitnum)
```


**Cleaning tat2 data**


```{r Cleaning tat2 data}
#Column for what study it is
tat2_7t <- tat2_7t %>%
  mutate(study = "tat2_7t")

tat2_pet <- tat2_pet %>%
  mutate(study = "tat2_pet")

#Combining studies 
tat2_full <- rbind(tat2_7t, tat2_pet)

#Removing weird columns and columns relating to cerebellum
tat2_full <- tat2_full %>% select(-"X", -"X.1", 
                                  -"NZMean_97",  -"NZcount_97", 
                                  -"NZMean_98",  -"NZcount_98",
                                  -"NZMean_99",  -"NZcount_99",
                                  -"NZMean_100", -"NZcount_100",
                                  -"NZMean_101", -"NZcount_101",
                                  -"NZMean_102", -"NZcount_102")

#Separating id column into "id" and "visit"
tat2_full <- tat2_full %>%
  mutate(id = str_extract(name, "\\d{5}"),
         rest.date = str_extract(name, "\\d{8}"))

#Removing "name" column
tat2_full <- tat2_full %>% select(-"name")

#Adding visit number number
tat2_full <- tat2_full %>%
  mutate(rest.date = as.Date(rest.date, format = "%Y%m%d")) %>%
  group_by(id) %>%
  arrange(rest.date) %>%
  mutate(visitnum_tat2 = dense_rank(rest.date))

#Removing obvious outlier 11487 visit 3 (check this)
tat2_full <- tat2_full %>%
  filter(!(id == "11487" & visitnum_tat2 == "3")) %>%
  filter(!(id == "10202" & visitnum_tat2 == "1"))
```


**NOTE: Should calculate weighted mean about here. Idea is so use number of voxels as weighting between hemispheres unique for each subject on each day.** Goal is to see whether averaging fixes some weirdness between hemis.


```{r Weighted Means}
#Test scripttt 69/77
tat2_full <- tat2_full %>%
  group_by(id, rest.date) %>%
  mutate(
   #Caudate
   cic_pre_caudate = weighted.mean(c(NZMean_69, NZMean_77), c(NZcount_69, NZcount_77)),
   cic_pos_caudate = weighted.mean(c(NZMean_70, NZMean_78), c(NZcount_70, NZcount_78)),
   #Accumbens
   cic_nacc = weighted.mean(c(NZMean_74, NZMean_82), c(NZcount_74, NZcount_82)),
   #GP
   cic_pallidum = weighted.mean(c(NZMean_71, NZMean_79), c(NZcount_71, NZcount_79)),
   #Putamen!
   cic_pre_dorsal_put = weighted.mean(c(NZMean_112, NZMean_116), c(NZcount_112, NZcount_116)),
   cic_pre_ventral_put = weighted.mean(c(NZMean_113, NZMean_117), c(NZcount_113, NZcount_117)),
   cic_pos_dorsal_put = weighted.mean(c(NZMean_114, NZMean_118), c(NZcount_114, NZcount_118)),
   cic_pos_ventral_put = weighted.mean(c(NZMean_115, NZMean_119), c(NZcount_115, NZcount_119))
   ) %>%
  ungroup
```
*cic_PreCaudate_L	cic2_1mm+tlrc	69*
*cic_PosCaudate_L	cic2_1mm+tlrc	70*
*cic_Globus_Pallidus_L	cic2_1mm+tlrc	71*
*cic_Globus_Pallidus_R	cic2_1mm+tlrc	79*
*cic_Accumbens_L	cic2_1mm+tlrc	74*
*cic_Accumbens_R	cic2_1mm+tlrc	82*
*cic_PreCaudate_R	cic2_1mm+tlrc	77*
*cic_PosCaudate_R	cic2_1mm+tlrc	78*
*cic_PreDorsalPutamen_R	cic2_1mm+tlrc	112	*
*cic_PreDorsalPutamen_L	cic2_1mm+tlrc	116*	
*cic_PreVentralPutamen_R	cic2_1mm+tlrc	113	*
*cic_PreVentralPutamen_L	cic2_1mm+tlrc	117*	
*cic_PosDorsalPutamen_R	cic2_1mm+tlrc	114	*
*cic_PosDorsalPutamen_L	cic2_1mm+tlrc	118*	
cic_PosVentralPutamen_R	cic2_1mm+tlrc	115	
cic_PosVentralPutamen_L	cic2_1mm+tlrc	119	

```{r Removing Columns}
tat2_full <- tat2_full %>%
  select(c("id", "study", "rest.date", 
"cic_pre_caudate", "cic_pos_caudate", "cic_nacc", "cic_pallidum", "cic_pre_dorsal_put", 
"cic_pre_ventral_put", "cic_pos_dorsal_put", "cic_pos_ventral_put"))

full <- full %>%
  select(c("id", "visitnum", "age", "rest.date", "behave.date", "sex", 
           "modelbased", "modelfree", "commonrare", "firststagestay", 
           "a1", "beta1", "a2", "beta2", "pi", "w", "lambda", 
           "harox_striatum", "harox_nacc", "harox_caudate", "harox_putamen", "harox_pallidum"))

tat2_full <- tat2_full %>%
  mutate(id = as.character(id))

full <- full %>%
  mutate(id = as.character(id))

tat2_full <- tat2_full %>%
  mutate(rest.date = as_date(rest.date))

full <- full %>%
  mutate(rest.date = as_date(rest.date))
```

Merging

```{r}
full_t <- full %>%
  left_join(tat2_full, by = c("id", "rest.date"))
```


**neuroCombat**

```{r neuroCombat}
temp_df <- full_t %>% 
  dplyr::select("id", "visitnum", "age",  "sex", 
"harox_striatum", 
"harox_nacc", "harox_caudate", "harox_putamen", "harox_pallidum", 
"study", "cic_pre_caudate", "cic_pos_caudate", "cic_nacc", "cic_pallidum", 
"cic_pre_dorsal_put", "cic_pre_ventral_put", "cic_pos_dorsal_put", 
"cic_pos_ventral_put") %>% 
  drop_na("id", "visitnum", "age", "sex", 
"harox_striatum", 
"harox_nacc", "harox_caudate", "harox_putamen", "harox_pallidum", 
"study", "cic_pre_caudate", "cic_pos_caudate", "cic_nacc", "cic_pallidum", 
"cic_pre_dorsal_put", "cic_pre_ventral_put", "cic_pos_dorsal_put", 
"cic_pos_ventral_put") %>% 
  distinct()

##hypothetical combat

temp_df$sex <- gsub("M", "1", temp_df$sex)
temp_df$sex <- gsub("F", "2", temp_df$sex)

temp_df$study <- gsub("tat2_7t", "1", temp_df$study)
temp_df$study <- gsub("tat2_pet", "2", temp_df$study)


## actual combat 

batch <- as.factor(temp_df$study)
mod1 <- as.factor(temp_df$sex)
mod2 <- as.numeric(temp_df$age)
id <- as.factor(temp_df$id)

mod <- model.matrix(~mod2+mod1)

temp_df_combat <- temp_df %>% 
  dplyr::select(-id, -study, -sex, -age, -visitnum)

temp_df_combat_t <- temp_df_combat %>% t %>% as.matrix

data.harmonized <- neuroCombat(dat=temp_df_combat_t, batch=batch, mod=mod)

temp_df_combat_t_harmonized <- data.harmonized$dat.combat  

temp_df_combat_harmonized <- temp_df_combat_t_harmonized %>% t %>% as.data.frame

#Append suffix to all columns in harmonized data.
colnames(temp_df_combat_harmonized) <-
  paste(colnames(temp_df_combat_harmonized), "_harm", sep = "")

test <- cbind(temp_df, temp_df_combat_harmonized)

full <- full %>% select(c("id", "visitnum", "age", "rest.date", "behave.date", "sex", 
"modelbased", "modelfree", "commonrare", "firststagestay", "a1", 
"beta1", "a2", "beta2", "pi", "w", "lambda", "harox_striatum", 
"harox_nacc", "harox_caudate", "harox_putamen", "harox_pallidum"
))
full_q <- merge(full, test, by = c("id", "visitnum"), all = TRUE)
dim(full)
length(unique(full$id))

#tat2_full_harm <- test

#Subsetting harmonized columns
#columns_to_select <- c("id", "age", "sex", "visitnum", "study")

#tat2_full_harm <- tat2_full_harm %>%
#  select(all_of(columns_to_select), ends_with("harm"))
```

*LONGER!!!*


```{r}
# Pivot longer
full_long <- full_q %>%
  pivot_longer(cols = ends_with("harm"), names_to = "roi", values_to = "beta")

#Rainclooud plot by scanner
lunaize(ggplot(full_long %>% 
         filter(complete.cases(.)), 
       aes(x = roi, y = beta, fill = roi)) + 
  geom_rain(alpha = 0.7) +
  theme_bw() +
  scale_y_continuous(trans = "reverse") +
  #scale_fill_brewer(palette = "Dark2") +
  guides(fill = "none", color = "none") +
  labs(x = "ROI", y = "nT2*w") +
  #scale_x_discrete(labels = custom_labels) +
    facet_wrap(~study))
```


```{r}
lunaize(ggplot(data = full_long %>% filter(roi == "cic_pre_caudate_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pos_caudate_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pallidum_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_nacc_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pre_dorsal_put_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pre_ventral_put_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pos_dorsal_put_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))

lunaize(ggplot(data = full_long %>% filter(roi == "cic_pos_ventral_put_harm"), 
                           aes(x=age.x, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: "))
```


**Model check**

```{r Model check}
mod_put_int <- gamm(cic_pos_dorsal_put_harm ~ 1 + sex.x + visitnum  +
                 s(age.x, k = 3, fx = T) +
                 s(modelbased, k = 3, fx = TRUE) +
                 s(firststagestay, k = 3, fx = TRUE),
                 random = list(id = ~1),
                 method = "REML",
                 data = full_q)
summary(mod_put_int$gam)
draw(mod_put_int)

plot(ggpredict(mod_put_int, terms = c("age.x", "modelbased"))) + scale_y_continuous(trans = "reverse")
plot(ggpredict(mod_put_int, terms = c("age.x", "firststagestay"))) + scale_y_continuous(trans = "reverse")

check <- gamm(modelfree ~ 1 + sex.x + visitnum + 
                s(age.x, k = 3, fx = TRUE) +
                s(age.x, by = cic_pos_ventral_put_harm, k = 3, fx = TRUE) +
                s(age.x, by = cic_pos_dorsal_put_harm, k = 3, fx = TRUE) +
                s(age.x, by = cic_pre_ventral_put_harm, k = 3, fx = TRUE) +
                s(age.x, by = cic_pre_dorsal_put_harm, k = 3, fx = TRUE),
              random = list(id = ~1),
              method = "REML",
              data = full_q)
summary(check$gam)
plot(ggpredict(check, terms = c("age.x", "cic_pos_caudate_harm")))
```

