---
title: "cic_tat2"
author: "Daniel Petrie"
date: "2024-06-21"
output:
  html_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

The script checks tat2 data between 7t and pet using the CIC atlas.


**ROIs for the CIC atlas**

- I will exclude the cerebellum but keep everything else. For a first pass, I think looking at both hemisphere

cic_PreCaudate_L	cic2_1mm+tlrc	69
cic_PosCaudate_L	cic2_1mm+tlrc	70
cic_Globus_Pallidus_L	cic2_1mm+tlrc	71
cic_Globus_Pallidus_R	cic2_1mm+tlrc	79
cic_Accumbens_L	cic2_1mm+tlrc	74
cic_Accumbens_R	cic2_1mm+tlrc	82
cic_PreCaudate_R	cic2_1mm+tlrc	77
cic_PosCaudate_R	cic2_1mm+tlrc	78
cic_PreDorsalPutamen_R	cic2_1mm+tlrc	112	
cic_PreDorsalPutamen_L	cic2_1mm+tlrc	116	
cic_PreVentralPutamen_R	cic2_1mm+tlrc	113	
cic_PreVentralPutamen_L	cic2_1mm+tlrc	117	
cic_PosDorsalPutamen_R	cic2_1mm+tlrc	114	
cic_PosDorsalPutamen_L	cic2_1mm+tlrc	118	
cic_PosVentralPutamen_R	cic2_1mm+tlrc	115	
cic_PosVentralPutamen_L	cic2_1mm+tlrc	119	

*Cerebellum*

cic_Dorsal_Cerebellum_R	cic2_1mm+tlrc	97
cic_Dorsal_Cerebellum_L	cic2_1mm+tlrc	98
cic_Ventrolateral_Cerebellum_R	cic2_1mm+tlrc	99	
cic_Ventrolateral_Cerebellum_L	cic2_1mm+tlrc	100	
cic_Medial_Cerebellum_R	cic2_1mm+tlrc	101	
cic_Medial_Cerebellum_L	cic2_1mm+tlrc	102


```{r Global}
library(ggplot2)
library(ggridges)
library(tidyverse)
library(dplyr)
library(neuroCombat)
library(LNCDR)
library(ggrain)

setwd("C:/Users/djpet/Documents/daw_resting_state")
tat2_7t <- read.delim("cleaning/7t_cic.tsv", header = TRUE)
tat2_pet <- read.delim("cleaning/pet_cic.tsv", header = TRUE)
merge_7t <- read.csv("cleaning/merged_7t.csv", header = TRUE)
merge_pet <- read.csv("cleaning/merged_pet.csv", header = TRUE)

#tat2_7t <- read.delim("cleaning/7t_cic_vox.tsv", header = TRUE)
#tat2_pet <- read.delim("cleaning/pet_cic_vox.tsv", header = TRUE)
```


**Cleaning tat2 data**


```{r Cleaning tat2 data}
#Column for what study it is
tat2_7t <- tat2_7t %>%
  mutate(study = "tat2_7t")

tat2_pet <- tat2_pet %>%
  mutate(study = "tat2_pet")

#Combining studies 
tat2_full <- rbind(tat2_7t, tat2_pet)

#Removing weird columns and columns relating to cerebellum
tat2_full <- tat2_full %>% select(-"X", -"X.1", 
                                  -"NZMean_97",  
                                  -"NZMean_98", 
                                  -"NZMean_99", 
                                  -"NZMean_100", 
                                  -"NZMean_101", 
                                  -"NZMean_102") 
#Separating id column into "id" and "visit"
tat2_full <- tat2_full %>%
  mutate(id = str_extract(name, "\\d{5}"),
         rest.date = str_extract(name, "\\d{8}"))

#Removing "name" column
tat2_full <- tat2_full %>% select(-"name")

#Adding visit number number
tat2_full <- tat2_full %>%
  mutate(rest.date = as.Date(rest.date, format = "%Y%m%d")) %>%
  group_by(id) %>%
  arrange(rest.date) %>%
  mutate(visitnum = dense_rank(rest.date))

#Removing obvious outlier 11487 visit 3 (check this)
tat2_full <- tat2_full %>%
  filter(!(id == "11487" & visitnum == "3")) %>%
  filter(!(id == "10202" & visitnum == "1"))

#Some cleaning for plotting
# age info
datereduce_7t <- merge_7t %>% 
  dplyr::select(lunaid, rest.date, rest.age, sex) %>%
  mutate(rest.date = as.Date(as.character(rest.date), format = "%Y%m%d")) %>%
  rename(id = lunaid,
         age = rest.age)

datereduce_pet <- merge_pet %>% 
  dplyr::select(lunaid, vdate, age, sex) %>%
  mutate(vdate = as.Date(as.character(vdate), format = "%Y%m%d")) %>%
  rename(id = lunaid,
         rest.date = vdate)
  
#Combining studies
datereduce_full <- rbind(datereduce_7t, datereduce_pet)

#Merging
tat2_full <- merge(tat2_full,datereduce_full,by=c('id','rest.date'))
```


**NOTE: Should calculate weighted mean about here. Idea is so use number of voxels as weighting between hemispheres unique for each subject on each day.** Goal is to see whether averaging fixes some weirdness between hemis.


```{r Weighted Means}
#Test scripttt 69/77
df_weighted_mean <- tat2_full %>%
  group_by(id, rest.date) %>%
  summarise(
    #weighted_mean1 = weighted.mean(NZMean_69, NZcount_69, na.rm = TRUE),
    #weighted_mean2 = weighted.mean(NZMean_77, NZcount_77, na.rm = TRUE),
    weighted_mean_combined = (sum(NZMean_69 * NZcount_69, na.rm = TRUE) + sum(NZMean_77 * NZcount_77, na.rm = TRUE)) / (sum(NZcount_69, na.rm = TRUE) + sum(NZcount_77, na.rm = TRUE))
  )
#Something like this should work. I'd just have to figure out how to do this for all variables in data set.
```



**tat2_full will be used for neurocombat.**


```{r}
new_names <- c("cic_PreCaudate_L", "cic_PosCaudate_L", "cic_Globus_Pallidus_L", "cic_Accumbens_L",
               "cic_PreCaudate_R", "cic_PosCaudate_R", "cic_Globus_Pallidus_R", "cic_Accumbens_R",
               "cic_PreDorsalPutamen_R", "cic_PreVentralPutamen_R", "cic_PosDorsalPutamen_R",
               "cic_PosVentralPutamen_R", "cic_PreDorsalPutamen_L", "cic_PreVentralPutamen_L",
               "cic_PosDorsalPutamen_L", "cic_PosVentralPutamen_L")


# Get the current names of the columns that start with "NZ"
nz_columns <- names(tat2_full) %>% str_subset("^NZ")

# Create a named vector for renaming
renaming_map <- setNames(nz_columns, new_names)

# Rename the columns
tat2_full <- tat2_full %>% rename(!!!renaming_map)
```


*LONGER!!!*


```{r}
# Pivot longer
tat2_full_long <- tat2_full %>%
  pivot_longer(cols = starts_with("cic"), names_to = "roi", values_to = "beta")
```


*Let's look at differences between 7t and pet before we harmonize.*


```{r Non-harmonized plots}
#Rainclooud plot by scanner
lunaize(ggplot(tat2_full_long %>% 
         filter(complete.cases(.)), 
       aes(x = roi, y = beta, fill = roi)) + 
  geom_rain(alpha = 0.7) +
  theme_bw() +
  scale_y_continuous(trans = "reverse") +
  #scale_fill_brewer(palette = "Dark2") +
  guides(fill = "none", color = "none") +
  labs(x = "ROI", y = "nT2*w") +
  #scale_x_discrete(labels = custom_labels) +
    facet_wrap(~study))
```


Ok. There seems to be some outliers still. Will look into this further. Also, there seems to be some minimal differences between 7t and pet.


**neuroCombat**

```{r neuroCombat}
temp_df <- tat2_full %>% 
  dplyr::select("id", "cic_PreCaudate_L", "cic_PosCaudate_L", 
"cic_Globus_Pallidus_L", "cic_Accumbens_L", "cic_PreCaudate_R", 
"cic_PosCaudate_R", "cic_Globus_Pallidus_R", "cic_Accumbens_R", 
"cic_PreDorsalPutamen_R", "cic_PreVentralPutamen_R", "cic_PosDorsalPutamen_R", 
"cic_PosVentralPutamen_R", "cic_PreDorsalPutamen_L", "cic_PreVentralPutamen_L", 
"cic_PosDorsalPutamen_L", "cic_PosVentralPutamen_L", "study", 
"visitnum", "age", "sex") %>% 
  drop_na("id", "cic_PreCaudate_L", "cic_PosCaudate_L", 
"cic_Globus_Pallidus_L", "cic_Accumbens_L", "cic_PreCaudate_R", 
"cic_PosCaudate_R", "cic_Globus_Pallidus_R", "cic_Accumbens_R", 
"cic_PreDorsalPutamen_R", "cic_PreVentralPutamen_R", "cic_PosDorsalPutamen_R", 
"cic_PosVentralPutamen_R", "cic_PreDorsalPutamen_L", "cic_PreVentralPutamen_L", 
"cic_PosDorsalPutamen_L", "cic_PosVentralPutamen_L", "study", 
"visitnum", "age", "sex") %>% 
  distinct()

##hypothetical combat

temp_df$sex <- gsub("M", "1", temp_df$sex)
temp_df$sex <- gsub("F", "2", temp_df$sex)

temp_df$study <- gsub("tat2_7t", "1", temp_df$study)
temp_df$study <- gsub("tat2_pet", "2", temp_df$study)


## actual combat 

batch <- as.factor(temp_df$study)
mod1 <- as.factor(temp_df$sex)
mod2 <- as.numeric(temp_df$age)
id <- as.factor(temp_df$id)

mod <- model.matrix(~mod2+mod1)

temp_df_combat <- temp_df %>% 
  dplyr::select(-id, -study, -sex, -age, -visitnum)

temp_df_combat_t <- temp_df_combat %>% t %>% as.matrix

data.harmonized <- neuroCombat(dat=temp_df_combat_t, batch=batch, mod=mod)

temp_df_combat_t_harmonized <- data.harmonized$dat.combat  

temp_df_combat_harmonized <- temp_df_combat_t_harmonized %>% t %>% as.data.frame

#Append suffix to all columns in harmonized data.
colnames(temp_df_combat_harmonized) <-
  paste(colnames(temp_df_combat_harmonized), "_harm", sep = "")

test <- cbind(temp_df, temp_df_combat_harmonized)

#full <- full %>% select("id", "visitnum", 
#                        "modelbased", "modelfree", "commonrare",
#                        "firststagestay", "winswitch", "modelfree_z", 
#                        "modelbased_z", "commonrare_z", 
#                        "firststagestay_z", "winswitch_z", 
#                        "modeldiff_z")
#
#
##full <- merge(full, test, by = c("id", "visitnum"))
#full <- merge(full, test, by = c("id", "visitnum"), all = TRUE)
#dim(full)
#length(unique(full$id))

tat2_full_harm <- test

#Subsetting harmonized columns
columns_to_select <- c("id", "age", "sex", "visitnum", "study")

tat2_full_harm <- tat2_full_harm %>%
  select(all_of(columns_to_select), ends_with("harm"))
```


*LONGER!*


```{r}
#Using grep to select columns I want.
columns_to_select <- grep("^(?!.*_z).*cic.*harm|harm.*cic", 
                          names(full), 
                          value = TRUE, 
                          perl = TRUE)

#Subsetting
tat2_full_harm <- full %>%
  select(id, visitnum, age, sex, study, all_of(columns_to_select))
#Pivot longer for raincloud plot.
tat2_full_long_harm <- pivot_longer(tat2_full_harm, 
                        cols = starts_with("cic"), 
                        names_to = "roi", 
                        values_to = "beta")
#Change back to words for plotting
tat2_full_long_harm <- tat2_full_long_harm %>%
  mutate(study = ifelse(study == "1", "tat2_7t", "tat2_pet"))

#Creating column for hemisphere based on values in "roi"
tat2_full_long_harm <- tat2_full_long_harm %>%
  mutate(hemi = case_when(
    str_detect(roi, "_L_") ~ "L",
    str_detect(roi, "_R_") ~ "R"
  ))

# Create the 'structure' column based on values in 'roi'
tat2_full_long_harm <- tat2_full_long_harm %>%
  mutate(structure = case_when(
    str_detect(roi, "Caudate") ~ "Caudate",
    str_detect(roi, "Putamen") ~ "Putamen",
    str_detect(roi, "Accumbens") ~ "Nacc",
   str_detect(roi, "Pallidus") ~ "Pallidus",
    TRUE ~ NA_character_
  ))
```


Post harmonized

```{r}
#Rainclooud plot by scanner
lunaize(ggplot(tat2_full_long_harm %>% 
         filter(complete.cases(.)), 
       aes(x = roi, y = beta, fill = roi)) + 
  geom_rain(alpha = 0.7) +
  theme_bw() +
  scale_y_continuous(trans = "reverse") +
  #scale_fill_brewer(palette = "Dark2") +
  guides(fill = "none", color = "none") +
  labs(x = "ROI", y = "nT2*w") +
  #scale_x_discrete(labels = custom_labels) +
    facet_wrap(~study))

#Raincloud plot for whole sample
lunaize(ggplot(tat2_full_long_harm %>% 
         filter(complete.cases(.)), 
       aes(x = roi, y = beta, fill = roi)) + 
  geom_rain(alpha = 0.7) +
  geom_rain(alpha = 0.7) +
  theme_bw() +
  scale_y_continuous(breaks = c(1.3, 1.2, 1.1, 1.0, 0.9, 
                                0.8, 0.7, 0.6, 0.5, 0.4), trans = "reverse") +
  #scale_fill_brewer(palette = "Dark2") +
  guides(fill = "none", color = "none") +
  labs(x = "ROI", y = "nT2*w"))
```

nT2*w trajectories by hemisphere and ROI.

```{r}
lunaize(ggplot(data = tat2_full_long_harm %>% filter(structure == "Caudate"), 
                           aes(x=age, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: ") + 
          facet_wrap(~hemi + study))

lunaize(ggplot(data = tat2_full_long_harm %>% filter(structure == "Nacc"), 
                           aes(x=age, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: ") + 
          facet_wrap(~hemi + study))

lunaize(ggplot(data = tat2_full_long_harm %>% filter(structure == "Pallidus"), 
                           aes(x=age, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: ") + 
          facet_wrap(~hemi + study))

lunaize(ggplot(data = tat2_full_long_harm %>% filter(structure == "Putamen"), 
                           aes(x=age, y=beta, colour = roi)) + 
                      theme_bw() + 
                      scale_y_continuous(trans = "reverse") + 
                      geom_smooth(method = "gam", 
                                  formula = y ~ s(x, bs = "tp"), 
                                  se = TRUE) + 
                      labs(x = "Age", y = "nT2*w", color = "ROI: ") + 
          facet_wrap(~hemi + study))
```

