---
title: "create_daw_txt_hBayesDM_val"
author: "Daniel Petrie"
date: "2024-08-01"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes Daw trial level data, does some cleaning, and saves a txt file to be used as input for hBayesDM.

Note: For Val I am running hBayesDM on entire 7t sample and for kids and adults. Output is three txt files.

```{r}
library(tidyverse)
library(dplyr)

#Working Directory
setwd("H:/Dan/rl_models/val")

#Read in data trial-level beh data
luna_7t <- read.csv("luna_7tbrainmech.csv", header = TRUE)

#Subject Ages
luna_7t_ages <- read.csv("merged_7t.csv", header = TRUE)
```

Recoding trial data to fit hBayesDM requirements. See documentation at https://ccs-lab.github.io/hBayesDM/reference/ts_par7.html

```{r}
luna_7t <- luna_7t %>% 
group_by(id) %>% 
mutate(trial = row_number()) %>% 
filter(choice1 != 0 & choice2 != 0) %>% 
rename(subjID = id, level1_choice = choice1, reward = money) %>% 
mutate(level2_choice = case_when(
level1_choice == 1 & choice2 == 1 & state == 2 ~ 1, 
level1_choice == 1 & choice2 == 2 & state == 2 ~ 2, 
level1_choice == 2 & choice2 == 1 & state == 3 ~ 3, 
level1_choice == 2 & choice2 == 2 & state == 3 ~ 4, 
level1_choice == 1 & choice2 == 1 & state == 3 ~ 3, 
level1_choice == 1 & choice2 == 2 & state == 3 ~ 4, 
level1_choice == 2 & choice2 == 1 & state == 2 ~ 1, 
level1_choice == 2 & choice2 == 2 & state == 2 ~ 2)) %>% 
  #remove duplicates
filter(!(subjID %in% c("11455_20181218", "11565_20190709")))
```

luna_7t can now be used for hBayesDM on full sample.

Checking amount of trials for each subject of each visit.

```{r}
subject_counts <- luna_7t %>%
  group_by(subjID) %>%
  dplyr::summarize(trial_count = n())
```

Extracting ages from merged_7t.csv

```{r}
luna_7t_ages <- luna_7t_ages %>%
  select(lunaid, behave.date, behave.age) %>%
  rename(subjID = lunaid)
```


Adding ages to luna_7t file

```{r}
#Seperating id and visit date for merging.
luna_7t_temp <- luna_7t %>%
  separate(subjID, c("subjID", "behave.date"))

#Making integer variable to allow left_join to work properly.
luna_7t_temp$subjID <- as.integer(luna_7t_temp$subjID)
luna_7t_temp$behave.date <- as.integer(luna_7t_temp$behave.date)

#Merge ages
luna_7t_full <- left_join(luna_7t_temp, luna_7t_ages, by = c("subjID", "behave.date"))
```

Create kids and adults data frames

```{r}
#Create a data frame for ages below 18
kids <- luna_7t_full %>%
  filter(behave.age < 18)

# Create a data frame for ages 18 and above
adults <- luna_7t_full %>%
  filter(behave.age >= 18)
```

Merging behave.date and subjID back together. This will allow hBayesDM to recognize that each subject has seperate visits (i.e., 200 trials each and not combining across visits!).

```{r}
# Create a new column by merging `id` and `date` with an underscore, then remove the original columns
kids <- kids %>%
  mutate(id_date = paste(subjID, behave.date, sep = "_")) %>%
  select(-subjID, -behave.date) %>%
  rename(subjID = id_date) %>%
  select(subjID, behave.age, trial, level1_choice, level2_choice, reward)

# Create a new column by merging `id` and `date` with an underscore, then remove the original columns
adults <- adults %>%
  mutate(id_date = paste(subjID, behave.date, sep = "_")) %>%
  select(-subjID, -behave.date) %>%
  rename(subjID = id_date) %>%
  select(subjID, behave.age, trial, level1_choice, level2_choice, reward)
```

Checking amount of trials for each subject of each visit.

```{r}
subject_counts_kids <- kids %>%
  group_by(subjID) %>%
  dplyr::summarize(trial_count = n())

subject_counts_adults <- adults %>%
  group_by(subjID) %>%
  dplyr::summarize(trial_count = n())
```


Saving .txt files

```{r}
#write.table(luna_7t, file = "luna_7t.txt", sep = "\t", row.names = FALSE)
write.table(kids, file = "kids.txt", sep = "\t", row.names = FALSE)
write.table(adults, file = "adults.txt", sep = "\t", row.names = FALSE)
```