---
title: "daw_analyses_061224"
author: "Daniel Petrie"
date: "2024-06-12"
output: html_document
editor_options: 
  chunk_output_type: console
---

WD/Libraries/data

```{r Global eval=FALSE}
library("ggplot2") #For plotting
library("GGally") #ggpairs()
library("tidyverse") #Wranglin
library("dplyr") #Wranglin
library("interactions")
library("lme4") #MLM
library("lmerTest") #p-vals
library("ggeffects") #For marginal/conditional effects plots
#library("margins") #For margins() function. Useful for comparing margins from ggeffects
library("marginaleffects") #For hypothesis_test()
library("parameters") #Other useful marginal effects functions
library("gdata") #upperTriangle()
library("mgcv") #GAMM
library("ggpubr") #Combining plots
library("bmlm") #Centering made easy
library("neuroCombat") #Harminization
library("LNCDR") #waterfall plot, lunaize plots 
library("gratia") #mgcv companion package. Using draw among other funcs.
#library("scales") #For Bart function
library("psych") #Descriptives
library("ggrain") #Raincloud plot
#library("corrplot") #Corrplot()
#Working directory (change to something better (onedrive?, something else?) at some point)
#Hera feels correct at this moment. All files could live in directory R for this project.
setwd("C:/Users/djpet/Documents/daw_resting_state")
full <- read.csv("daw_project_060524.csv", header = TRUE)
```

11475 visit 2 should be removed.
11498 visit 2 should be removed.
11589 visit 2 should be removed.


Cleaning


```{r Cleaning}
#Creating a different sex variable for some plots/analyses
full <- full %>%
  mutate(sex = as.character(sex),
    sex_p = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female",
    TRUE ~ sex 
  ))

#Making visitnum a factor. Can change accordingly
full$visitnum <- as.factor(full$visitnum)

#Making sex a factor
full$sex <- as.factor(full$sex)

#Making an ordered factor.
full$sex_p <- ordered(full$sex_p, levels = (c("Male", "Female")))

#Inverse age for linear models.
full$inv_age <- 1/full$age

#Checking for duplicate rows due to weird merging situation I put myself in.
full[which(duplicated(full$modelbased)),c(1:3, 8, 20)] #11475_2/11498_2/11589_2 are duplicates.
#These ids have duplicated Daw visits, but different rest days. Taking rows with imaging data.

full <- full %>%
  filter(!(id == "11475" & visitnum == "2") & 
           !(id == "11498" & visitnum == "2") &
           !(id == "11589" & visitnum == "2"))

#Treating visitnum as numeric?
full$visitnum_numeric <- as.numeric(full$visitnum)

#Residualizing out age effects in Daw variables.
#can be removed.
fss_resid <- lm(firststagestay ~ 1 + age, data = full, na.action = na.exclude)
full$fss_resid <- resid(fss_resid)
full$fss_resid_z <- scale(full$fss_resid)

mb_resid <- lm(modelbased ~ 1 + age, data = full, na.action = na.exclude)
full$mb_resid <- resid(mb_resid)
full$mb_resid_z <- scale(full$mb_resid)

mf_resid <- lm(modelfree ~ 1 + age, data = full, na.action = na.exclude)
full$mf_resid <- resid(mf_resid)
full$mf_resid_z <- scale(full$mf_resid)


put_resid <- lm(harox_putamen_harm ~ 1 + age, data = full, na.action = na.exclude)
full$harox_putamen_harm_resid <- resid(put_resid)
full$harox_putamen_harm_resid_z <- scale(full$harox_putamen_harm_resid)
```

NOTE: Zero-order correlations, means, SD, of all study variables will be done in another script. ML LR results of the analytic sample, as well as general behavioral results have been conducted in another script. The purpose of this script is to analyze the Daw RL parameters, iron measures, and age. I can also add the cic atlas analyses here to be included in the supplement.


# **Data Analyses Plan**


## **Replication Analyses**


We replicate previous work examining age trajectories of nT2*w in the NAcc, globus pallidus, caudate, and putamen (CITE). We used four separate generalized additive mixed models that were specified as follows:


$$

nT2^*w_{i,t} = \beta_0 + \beta_1{sex}_{i} + \beta_2{visit}_{i,t} + f(\text{age}_{i,t}) + b_{0i} + \epsilon_{i,t}, \quad e \sim N(0,\sigma^2)   

$$
where $$nT2^*w_{i,t}$$ is the iron value for person $$i$$ on visit $$t$$. $$\beta_0$$ is the overall intercept of $$nT2*w$$, $$\beta_1$$ and $$\beta_2$$ are covariates for sex assigned at birth and visit number, respectively. $$f$$ represents a smooth function of age for the $$t$$-th repeated measure of the $$i$$-th individual. $$b_{0i}$$ represents the random intercept term for the $$i$$-th individual. All models were fit with 3 knots (i.e., k = 3) and unpenalized splines (i.e., all smoothing parameters are fixed to 0; fx = TRUE). We applied the Bonferroni correction to account for multiple comparisons ($$\alpha < 0.0125$$ uncorrected).


## Fitting the GAMMs and adjusting for multiple comparrisons.


```{r nT2*w ~ s(age) results}
#pallidum
pallidum_age <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(pallidum_age$lme)
summary(pallidum_age$gam)

#Figure
draw(pallidum_age) +  scale_y_continuous(trans = "reverse")

#P-value test
summary(pallidum_age$gam)$s.table[4] < 0.05/4

#Nacc
nacc_age <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(nacc_age$lme)
summary(nacc_age$gam)

#Figure
draw(nacc_age) +  scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_age$gam)$s.table[4] < 0.05/4

#caudate
ca_age <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(ca_age$lme)
summary(ca_age$gam)

#Figure
draw(ca_age) +  scale_y_continuous(trans = "reverse")

#Interesting shape to plot derivative (i.e., not a line)
draw(derivatives(ca_age)) + scale_y_continuous(trans = "reverse") 

#P-value test
summary(ca_age$gam)$s.table[4] < 0.05/4

#putamen
put_age <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(put_age$lme)
summary(put_age$gam)

#Figure
draw(put_age) +  scale_y_continuous(trans = "reverse")

#P-value test
summary(put_age$gam)$s.table[4] < 0.05/4
```


**All age smooths are significantly different than 0. Additionally, they are all positively associated with nT2*w such that as age increases, nT2*w increases.**


## **Associations between RL parameters and age**


Next, we examined the age trajectories of the RL parameters derived from the multilevel logistic regression model. We replicate previous work showing that the model based parameter increased across age (Decker et al., YEAR). Additionally, we examined age trajectories of the model free parameter and the first stage stay parameter. We used three separate generalized additive mixed models that were specified as follows:

$$

RL_{i,t} = \beta_0 + \beta_1{sex}_{i} + \beta_2{visit}_{i,t} + f(\text{age}_{i,t}) + b_{0i} + \epsilon_{i,t}, \quad e \sim N(0,\sigma^2)   

$$
where $$RL_{i,t}$$ is the RL parameter value for person $$i$$ on visit $$t$$. All other variables are specified and estimated identically as equation ##. We applied the Bonferroni? correction to account for multiple comparisons ($$\alpha < 0.0167$$ uncorrected).


## Fitting the GAMMs and adjusting for multiple comparrisons.

```{r Daw ~ s(age) results}
#fss
fss_age <- gamm(firststagestay ~ 1 + sex + visitnum_numeric +
                         s(age, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(fss_age$lme)
summary(fss_age$gam)

#Figure
draw(fss_age)

#P-value test
summary(fss_age$gam)$s.table[4] < 0.05/4


#mb
mb_age <- gamm(modelbased ~ 1 + sex + visitnum_numeric +
                         s(age, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(mb_age$lme)
summary(mb_age$gam)

#Figure
draw(mb_age)

#P-value test
summary(mb_age$gam)$s.table[4] < 0.05/4


#mf
mf_age <- gamm(modelfree ~ 1 + sex + visitnum_numeric +
                         s(age, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(mf_age$lme)
summary(mf_age$gam)

#Figure
draw(mf_age)

#P-value test
summary(mf_age$gam)$s.table[4] < 0.05/4
```


**All age smooths are significantly different than 0. Additionally, they are all positively associated with RL such that as age increases, RL parameters increase. Important to note that for FSS and MB, there is a main effect of age, such that males have higher values than females controlling for age and experience with the task (i.e., visit number covariate inclusion).**


## **Associations between RL parameters and nT2*w**

Next, we want to see if there is any relationship between the iron measures and the RL parameters. Including age in these equations would more than likely render each effect non-significant, so I will not include them now.

Insert equation once finalized


```{r Bivariate Main Effects (NO AGE)}
#Caudate model based
ca_mb <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                         s(modelbased_z, k = 3, fx = TRUE) +
                s(id, bs = "re"),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_mb$lme)
summary(ca_mb$gam)

#Figure
draw(ca_mb) + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_mb$gam)$s.table[4] < 0.05/12


#Caudate model free
ca_mf <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                         s(modelfree_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_mf$lme)
summary(ca_mf$gam)

#Figure
draw(ca_mf) + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_mf$gam)$s.table[4] < 0.05/12

#Caudate fss
ca_fss <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                         s(firststagestay_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_fss$lme)
summary(ca_fss$gam)

#Figure
draw(ca_fss) + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_fss$gam)$s.table[4] < 0.05/12

#NACC model based
nacc_mb <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                         s(modelbased_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_mb$lme)
summary(nacc_mb$gam)

#Figure
draw(nacc_mb) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_mb$gam)$s.table[4] < 0.05/12


#nacc model free
nacc_mf <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                         s(modelfree_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_mf$lme)
summary(nacc_mf$gam)

#Figure
draw(nacc_mf) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_mf$gam)$s.table[4] < 0.05/12

#nacc fss
nacc_fss <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                         s(firststagestay_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_fss$lme)
summary(nacc_fss$gam)

#Figure
draw(nacc_fss) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_fss$gam)$s.table[4] < 0.05/12


#pallidum model based
gp_mb <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                         s(modelbased_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_mb$lme)
summary(gp_mb$gam)

#Figure
draw(gp_mb) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_mb$gam)$s.table[4] < 0.05/12


#pallidum model free
gp_mf <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                         s(modelfree_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_mf$lme)
summary(gp_mf$gam)

#Figure
draw(gp_mf) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_mf$gam)$s.table[4] < 0.05/12

#pallidum fss
gp_fss <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                         s(firststagestay_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_fss$lme)
summary(gp_fss$gam)

#Figure
draw(gp_fss) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_fss$gam)$s.table[4] < 0.05/12


#putamen model based
put_mb <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                         s(modelbased_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_mb$lme)
summary(put_mb$gam)

#Figure
draw(put_mb) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_mb$gam)$s.table[4] < 0.05/12


#putamen model free
put_mf <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                         s(modelfree_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_mf$lme)
summary(put_mf$gam)

#Figure
draw(put_mf) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_mf$gam)$s.table[4] < 0.05/12

#putamen fss
put_fss <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                         s(firststagestay_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_fss$lme)
summary(put_fss$gam)

#Figure
draw(put_fss) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_fss$gam)$s.table[4] < 0.05/12
```

No associations with caudate/Nacc and the Daw parameters. For pallidum and putamen, MF and FSS were associated (as MF and FSS increase, pallidum iron increases).

All of this is fine, but we want to see the relationships among Daw parameters, iron measures, and age. First I will look at main effects.

```{r Main Effects (Yes AGE)}
#Caudate model based
ca_mb_age <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                    s(age, k = 3, fx = TRUE) +
                         s(mb_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_mb_age$lme)
summary(ca_mb_age$gam)

#Figure
draw(ca_mb_age)# + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_mb_age$gam)$s.table[2,4] < 0.05/12


#Caudate model free
ca_mf_age <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                 s(age, k = 3, fx = TRUE) +
                         s(mf_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_mf_age$lme)
summary(ca_mf_age$gam)

#Figure
draw(ca_mf_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_mf_age$gam)$s.table[2,4] < 0.05/12

#Caudate fss
ca_fss_age <- gamm(harox_caudate_harm ~ 1 + sex + visitnum_numeric +
                  s(age, k = 3, fx = TRUE) +
                         s(fss_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(ca_fss_age$lme)
summary(ca_fss_age$gam)

#Figure
draw(ca_fss_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(ca_fss_age$gam)$s.table[2,4] < 0.05/12

#NACC model based
nacc_mb_age <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                   s(age, k = 3, fx = TRUE) +
                         s(mb_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_mb_age$lme)
summary(nacc_mb_age$gam)

#Figure
draw(nacc_mb_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_mb_age$gam)$s.table[2,4] < 0.05/12


#nacc model free
nacc_mf_age <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                   s(age, k = 3, fx = TRUE) +
                         s(mf_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_mf_age$lme)
summary(nacc_mf_age$gam)

#Figure
draw(nacc_mf_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_mf_age$gam)$s.table[2,4] < 0.05/12

#nacc fss
nacc_fss_age <- gamm(harox_nacc_harm ~ 1 + sex + visitnum_numeric +
                    s(age, k = 3, fx = TRUE) +
                         s(fss_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(nacc_fss_age$lme)
summary(nacc_fss_age$gam)

#Figure
draw(nacc_fss_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(nacc_fss_age$gam)$s.table[2,4] < 0.05/12


#pallidum model based
gp_mb_age<- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                 s(age, k = 3, fx = TRUE) +
                         s(mb_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_mb_age$lme)
summary(gp_mb_age$gam)

#Figure
draw(gp_mb_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_mb_age$gam)$s.table[2,4] < 0.05/12


#pallidum model free
gp_mf_age <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                 s(age, k = 3, fx = TRUE) +
                         s(mf_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_mf_age$lme)
summary(gp_mf_age$gam)

#Figure
draw(gp_mf_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_mf_age$gam)$s.table[2,4] < 0.05/12

#pallidum fss
gp_fss_age <- gamm(harox_pallidum_harm ~ 1 + sex + visitnum_numeric +
                  s(age, k = 3, fx = TRUE) +
                         s(fss_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(gp_fss_age$lme)
summary(gp_fss_age$gam)

#Figure
draw(gp_fss_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(gp_fss_age$gam)$s.table[2,4] < 0.05/12


#putamen model based
put_mb_age <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                  s(age, k = 3, fx = TRUE) +
                         s(mb_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_mb_age$lme)
summary(put_mb_age$gam)

#Figure
draw(put_mb_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_mb_age$gam)$s.table[2,4] < 0.05/12


#putamen model free
put_mf_age <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                  s(age, k = 3, fx = TRUE) +
                         s(mf_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_mf_age$lme)
summary(put_mf_age$gam)

#Figure
draw(put_mf_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_mf_age$gam)$s.table[2,4] < 0.05/12

#putamen fss
put_fss_age <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                   s(age, k = 3, fx = TRUE) +
                         s(fss_resid_z, k = 3, fx = TRUE),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(put_fss_age$lme)
summary(put_fss_age$gam)

#Figure
draw(put_fss_age) + scale_y_continuous(trans = "reverse")

#P-value test
summary(put_fss_age$gam)$s.table[2,4] < 0.05/12
```

After controlling for age, any association between nT2*w and Daw parameters are not significant. The effect of age is quite large.


```{r Exploratory Interactions}
#
t <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
            s(age, k = 3, fx = T) +
            s(age, by = fss_resid_z, k = 3, fx = T),                      
          random = list(id = ~1),
                      method = "REML",
          #na.action = na.exclude,
                      data = full)
summary(t$gam)
draw(t)


t1 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
            s(age, k = 3, fx = T) +
            s(age, by = modelbased_z, k = 3, fx = T),                      
          random = list(id = ~1),
                      method = "REML",
          #na.action = na.exclude,
                      data = full)
summary(t1$gam)
draw(t1)

t2 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
            s(age, k = 3, fx = T) +
            s(age, by = modelfree_z, k = 3, fx = T),                      
          random = list(id = ~1),
                      method = "REML",
          #na.action = na.exclude,
                      data = full)
summary(t2$gam)
draw(t2)



#Messing around with interactions as fixed effects.
q <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
            s(age, k = 3, fx = T) + firststagestay_z + firststagestay_z:age,
            #s(age, by = firststagestay_z, k = 3, fx = T),                      
          random = list(id = ~1),
                      method = "REML",
          #na.action = na.exclude,
                      data = full)
summary(q$gam)

#Model that works
test_3 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE) +
                 s(firststagestay_z, k = 3, fx = TRUE) +
                 s(modelbased_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_3$gam)


#Model with time-varying parameters
test_3 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE) +
                 s(age, by = fss_resid_z, k = 3, fx = TRUE) +
                 s(age, by = mb_resid_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(test_3$gam)




#b <- derivatives(test_3$gam)
#draw(t)
b <- ggpredict(test_3, terms = c("age[all]", "fss_resid_z[-2,2]"))
#c <- ggpredict(t, terms = c("age[10, 12, 15, 18, 20,25,30]", "modelbased_z[-1,0,1]"))

plot(b, show_data = TRUE) + scale_y_continuous(trans = "reverse")

ggplot(b, aes(x = group, y = predicted, group = group)) +
  geom_point() +
  geom_line(group = 1) +
  facet_wrap(~x, nrow = 1) +
  scale_y_continuous(trans = "reverse") +
  labs(x = "Habitual Behavior at mean (0) and +/- 1 SD",
       y = "Predicted Putamen nT2*w")

ggplot(c, aes(x = group, y = predicted, group = group)) +
  geom_point() +
  geom_line(group = 1) +
  facet_wrap(~x, nrow = 1) +
  scale_y_continuous(trans = "reverse") +
  labs(x = "Goal-directed Behavior at mean (0) and +/- 1 SD",
       y = "Predicted Putamen nT2*w")


# +
#            s(age, by = modelbased_z, k = 3, fx = T) +
#            s(age, by = modelfree_z, k = 3, fx = T)
```


NOTE: REML is used to compare models with nested random effects and the same fixed effects structure. ML to compare model with nested fixed effects and the same random effect structure. There is ample literature supporting this choice. Douglas Bates discusses it here https://cran.r-project.org/web/packages/lme4/vignettes/Theory.pdf 

```{r Model Comparrisons}
#Maybe model comparison?
test_1 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_1$gam)
summary(test_1$lme)

test_2 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE) +
                 s(fss_resid_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_2$gam)

test_3 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE) +
                 s(fss_resid_z, k = 3, fx = TRUE) +
                 s(mb_resid_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_3$gam)

test_4 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric + 
                       s(age, k = 3, fx = TRUE) +
                 s(fss_resid_z, k = 3, fx = TRUE) +
                 s(mb_resid_z, k = 3, fx = TRUE) +
                 s(mf_resid_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_4$gam)

# Compare models using anova function
anova(test_1$lme, 
      test_2$lme, 
      test_3$lme, 
      test_4$lme
      )
#Figure this weirdness out... difference between AIC and anova results.
b <- c(AIC(test_1$lme, 
           test_2$lme, 
           test_3$lme, 
           test_4$lme
           ))
which.min(b[[2]])

plot(ggpredict(test_3, terms = c("fss_resid_z"))) + scale_y_continuous(trans = "reverse")
```

Model comparisons suggest that model 3 is the best model using AIC. BIC hates parameters so it favors model 1. Logliklihood ratio tests suggests that model 

```{r Mediation}
#Treating visitnum as numeric?
full$visitnum_numeric <- as.numeric(full$visitnum)
#a path, indirect effect
m2 <- gam(harox_putamen_harm_z ~ 1 + sex  + visitnum_numeric +
            s(age_z, k = 3, fx = TRUE) + s(id, bs = "re"), 
          method = "REML", 
          data = full)
summary(m2)

m3 <- gam(firststagestay ~ 1 + sex + visitnum_numeric + 
             s(harox_putamen_harm_z, k = 3, fx = TRUE) +
             s(age_z, k = 3, fx = TRUE) + s(id, bs = "re"),
          method = "REML", 
          data = full)
summary(m3)

m2 <- lm(harox_putamen_harm_z ~ 1 +  sex + visitnum_numeric + inv_age, data = full, na.action = na.exclude)
summary(m2)
m3 <- lm(firststagestay ~ 1 + sex + visitnum_numeric + inv_age + harox_putamen_harm_z, data = full, na.action = na.exclude)
summary(m3)

#Note that visitnum messes things up. Perhaps change to factor/numeric?
#Testing moderated mediation models. Looking at "high habit" people.
#high_habit <- mean(full$firststagestay_z) - sd(full$firststagestay_z)

testing <- mediation::mediate(m2, m3, 
                              treat = "inv_age",
                   mediator = "harox_putamen_harm_z", 
                   boot = T, 
                   sims = 2000)
summary(testing)
plot(testing)

#Sensitivity check
sens.out <- medsens(testing, rho.by = 0.1, effect.type = "indirect", sims = 100)
summary(sens.out)
```


```{r Messing around}
test_3 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                       s(age, k = 3, fx = TRUE) +
                 s(firststagestay_z, k = 3, fx = TRUE) +
                 ti(age, firststagestay_z, k = 3, fx = TRUE) +
                 s(modelbased_z, k = 3, fx = TRUE) +
                 ti(age, modelbased_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(test_3$gam)
plot(ggpredict(test_3, terms = c("modelbased_z","age[10,15,20,25,30]"))) + scale_y_continuous(trans = "reverse")
plot(ggpredict(test_3, terms = c("firststagestay_z", "age[10,15,20,25,30]"))) + scale_y_continuous(trans = "reverse")

test_3 <- gamm(harox_putamen_harm ~ 1 + sex + visitnum_numeric  +
                       s(age, k = 3, fx = TRUE) +
                 s(firststagestay_z, k = 3, fx =TRUE) +
                 ti(age, firststagestay_z, k = 3, fx = TRUE),
                     random = list(id = ~1),
                     method = "ML",
                     data = full)
summary(test_3$gam)

put_age_fss <- gam(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                       s(age_z, k = 3, fx = TRUE) +
                      s(firststagestay_z, k = 3, fx = TRUE) +
                     s(modelbased_z, k = 3, fx = T) +
                     ti(age,firststagestay_z) +
                     s(id, bs = "re", k = 3, fx = T),
                     method = "REML",
                     data = full)
summary(put_age_fss)


pred <- predict_response(put_age_fss, terms = c("age_z", "firststagestay_z[-2,-1,0,1,2]"))
print(pred, collapse_tables = TRUE)
plot(pred, show_data = TRUE) + scale_y_continuous(trans = "reverse")
#Trying to get ash plot...
#Might be easier with gratia
ggplot(pred, aes(x = predicted, y = group)) + geom_point()

fd <- derivatives(put_age_fss)
ggplot(fd %>% filter(.smooth == "s(age_z):firststagestay_z"), aes(x = age_z, y = .derivative, group = .smooth)) +
  geom_line() +
  geom_ribbon(aes(ymin = .lower_ci, ymax = .upper_ci), alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(trans = "reverse")

spotlight_analysis(pred)

johnson_neyman(pred)

plot(johnson_neyman(pred)) + scale_y_continuous(trans = "reverse")


plot(predict_response(put_age_fss, terms = c("age_z", "firststagestay_z[-2,-1,1,0,1,2]")), show_data = T) + 
  scale_y_continuous(trans = "reverse") 
#+ 
#  geom_point(data = full, aes(x = age_z, y = harox_putamen_harm))

#Minimum velocity playing around
plot_slopes(put_age_fss, variables = "firststagestay_z", slope = "eyex", condition = c("age_z", "firststagestay_z")) + scale_y_continuous(trans = "reverse")


smh <- gamm(firststagestay ~ 1 + sex + visitnum_numeric +
              s(age_z, k = 3, fx = TRUE) +
              s(harox_putamen_harm_resid_z, k = 3, fx = TRUE) #+
              #s(harox_caudate_harm, k = 3, fx = TRUE) #+
              #s(harox_nacc_harm, k = 3, fx = TRUE) #+
              #s(harox_pallidum_harm, k = 3, fx = TRUE)
            ,
            random = list(id = ~1),
                     method = "REML",
                     data = full)
summary(smh$gam)

full$pred <- predict.gam(t$gam)
full$resid <- residuals(t$gam)

ggplot(full, aes(x = age, y = residuals.gam(t$gam), group = id)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(trans = "reverse") +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5)


plot(ggpredict(t, terms = c("firststagestay_z", "age[10,15,20,25,30]")), show_data = T) + scale_y_continuous(trans = "reverse")
plot(ggpredict(t, terms = c("age", "harox_putamen_harm_z"))) + scale_y_continuous(trans = "reverse")
plot(ggpredict(t, terms = c("firststagestay_z"))) + scale_y_continuous(trans = "reverse")
draw(t) + scale_y_continuous(trans = "reverse")
t <- gamm(firststagestay ~ 1 + sex + visitnum_numeric +
            s(age, k = 3, fx = T) +
            s(age, by = harox_putamen_harm_resid_z, k = 3, fx = T),
            #             s(harox_nacc_harm_z, k = 3, fx = F) +
            #s(harox_caudate_harm_z, k = 3, fx = F) +
            #s(harox_pallidum_harm_z, k = 3, fx = F),
           #s(id, bs = "re"),
                      random = list(id = ~1),
                      method = "REML",
                      data = full)
summary(t$gam)
plot(ggpredict(t, terms = c("age", "harox_putamen_harm_resid_z[-2,-1,0,1,2]")))
k.check(t$gam)
concurvity(t$gam)
```

```{r MOre sillyness}
#Comparing predictions with random intercepts and without random intercepts.
test <- full %>% group_by(id) %>% filter(n() == 3)

no_randint <- gam(harox_putamen_harm ~ 1 + age:sex + s(id, bs = "re") + s(id,age, bs = "re"), 
                  method = "REML", 
                  data = test, 
                  na.action = na.exclude)
summary(no_randint)
#Extract predicted values
new_data <- tidyr::expand(test, nesting(id, age),
                          sex = unique(sex))


##test$pred_no_randint <- predict.gam(no_randint)
#predictions <- predict(no_randint, newdata = test, se.fit = TRUE)
#test$pred <- predictions$fit
#Plot
ggplot(test, aes(x = age_z, y = pred, group = id)) +
  geom_point() +
  geom_line(aes(colour = id)) +
  stat_smooth(method = "gam", aes(group = 1))


put_age_fss <- gam(harox_putamen_harm ~ 1 + sex + visitnum_numeric +
                       s(age_z, k = 3, fx = TRUE) +
                     s(id, bs = "re", k = 3, fx = T),
                     method = "REML",
                     data = full,
                   na.action = na.exclude)
summary(put_age_fss)

full$pred <- predict.gam(put_age_fss)

ggplot(full, aes(x = age_z, y = pred, group = id)) +
  geom_point() +
  geom_line() +
  stat_smooth(method = "gam", aes(group = 1))
```

