---
title: "daw_stan_script"
author: "Daniel Petrie"
date: "2024-04-10"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r}
library(hBayesDM)
library(rstan)
library(tidyverse)
library(dplyr)
library(ggplot2)
setwd("C:/Users/djpet/Documents/daw_resting_state")
```

Cleaning Daw task data.

Only 4 columns of data are needed. There can be other columns included in the data frame. They must be labeled correctly for the package to work.

- "subjID"
- "level1_choice"
- "level2_choice"
- "reward"

More specific information below:

subjID
A unique identifier for each subject in the data-set.

level1_choice
Choice made for Level (Stage) 1 (1: stimulus 1, 2: stimulus 2).

level2_choice
Choice made for Level (Stage) 2 (1: stimulus 3, 2: stimulus 4, 3: stimulus 5, 4: stimulus 6).
Note that, in our notation, choosing stimulus 1 in Level 1 leads to stimulus 3 & 4 in Level 2 with a common (0.7 by default) transition. Similarly, choosing stimulus 2 in Level 1 leads to stimulus 5 & 6 in Level 2 with a common (0.7 by default) transition. To change this default transition probability, set the function argument `trans_prob` to your preferred value.

reward
Reward after Level 2 (0 or 1).

NOTE: ALL OF THIS IS NOW ON HERA! IT TAKES FAR TOO LONG TO RUN LOCALLY!

```{r}
luna_7t <- read.csv("luna_7tbrainmech.csv", header = TRUE)
luna_pet <- read.csv("luna_pet.csv", header = TRUE)
luna_full <- rbind(luna_7t, luna_pet)
length(unique(luna_full$id)) #416 subjects
#Subject 11455 has 400 trials. Not sure why, so removing for now. If they have neuroimaging data, consider taking first 200 trials?
#trials_per_subject <- luna_full%>% 
#  group_by(id) %>% 
#  summarise(trial_count = n())

#Let's just try with luna_pet first
#Adding trial number
luna_full <- luna_full %>%
  group_by(id) %>%
  mutate(trial = row_number()) %>%
  filter(choice1 != 0 & choice2 != 0) %>%
  rename(subjID = id,
         level1_choice = choice1,
         reward = money) %>% 
  mutate(level2_choice = case_when(
    level1_choice == 1 & choice2 == 1 & state == 2 ~ 1,
    level1_choice == 1 & choice2 == 2 & state == 2 ~ 2,
    level1_choice == 2 & choice2 == 1 & state == 3 ~ 3,
    level1_choice == 2 & choice2 == 2 & state == 3 ~ 4,
    level1_choice == 1 & choice2 == 1 & state == 3 ~ 3,
    level1_choice == 1 & choice2 == 2 & state == 3 ~ 4,
    level1_choice == 2 & choice2 == 1 & state == 2 ~ 1,
    level1_choice == 2 & choice2 == 2 & state == 2 ~ 2)) %>% 
    filter(!(subjID %in% c("11455_20181218", "11565_20190709")))
length(unique(luna_full$subjID)) #414

#Some script to make luna_full a .txt file.
```

In hBayesDM package, there are three different flavors of RL models, where the biggest difference is the number of estimated parameters.

4 parameter model:
- alpha (learning rate for both stages 1 & 2)
- beta (inverse temp for both stages 1 & 2)
- pi (perseverance)
- w (model-based weight)

6 parameter model:
- alpha1
- alpha2
- beta1
- beat2
- pi
- w

7 parameter model (oringinal Daw model; Daw et al., 2011):
- alpha1
- alpha2
- beta1
- beat2
- pi
- w
- eligibility trace


Lets look at the simplest model first.

Started appox 239 pm

```{r}
#test <- ts_par4(data = luna_pet, inc_postpred = TRUE)
```


Looking at hBayesDM output.

```{r}
bayes <- readRDS("ts_par4_test_results.rds")

#Basic graphs of full model
#Posterior distribution of hyper parameter.
plot(bayes)

#Diagnostic mustache plot for MCMC performace of hyper parameters.
plot(bayes, type = "trace")

#Include "burn in" or warmpup MCMC samples 
plot(bayes, type = "trace", inc_warmup = TRUE)

#For hyper parameters (Not sure what sigma is referring to just yet)
plotInd(bayes)

#For individual level plots.
plotInd(bayes, "pi") #Replace with whatever parameter was estimated.
plotInd(bayes, "w")
plotInd(bayes, "beta")
```

Compare models can be done using Leave-One-Out information criteria (LOOIC) or Widely Applicable INformation Criterion (WAIC).

```{r}
#Default is LOOIC
printFit(model1, model2, model3, model4)
printFit(bayes, ic = "both")
```


Posterior predictive checks:

ELI5: Posterior predictive checks are when a fitted model is used to generate simulated data and check if simulated data are similar to actual data. It answers the questions "Does my model generate valid predictions?"

Make sure to set inc_postpred = TRUE to get these. Is seems to increase run time AND increase file size.

```{r}
##example
#bayes_ex <- ts_par4("example",
#                    niter = 2000,
#                    nwarmup = 1000,
#                    inc_postpred = TRUE)
##dimensions of predicted values.
#dim(bayes_ex$parVals$y_pred_step1) #4000 MCMC samples x 11 subjects x 200 trials
#dim(bayes_ex$parVals$y_pred_step2)
#
##Averaging the 4000 MCMC samples, we will just look at step 1.
#y_pred_mean <- apply(bayes_ex$parVals$y_pred_step2, c(2,3), mean)
#
#dim(y_pred_mean) #11 subjects x 200 trials
#
##Number of subjects
#numSubjs <- dim(bayes_ex$allIndPars)[1]
#
##Create list of subject ids
##Get max number of trials
##True data
#subjList <- unique(bayes_ex$rawdata$subjID)
#maxT <- max(table(bayes_ex$rawdata$subjID))
#true_y <- array(NA, c(numSubjs, maxT))
#
#
##True data for each subject
##THe dimensions are off here. Figure that out at somepoint to run these.
#for (i in 1:numSubjs) {
#  tmpID = subjList[i]
#  tmpData = subset(bayes_ex$rawdata, subjID == tmpID)
#  true_y[i,] = tmpData$level2_choice
#}
#
### Subject #1
#plot(true_y[1, ], type="l", xlab="Trial", ylab="Choice (0 or 1)", yaxt="n")
#lines(y_pred_mean[1,], col="red", lty=2)
#axis(side=2, at = c(0,1) )
#legend("bottomleft", legend=c("True", "PPC"), col=c("black", "red"), lty=1:2)
```



Ok I want to mess around with these parameters, I should bring in age, and the neuro measures and see what those look like.

First, some notes on the contents of the hBayesDM object.

allindPars: Each subjects parameters, it also has the hyper parameters.

parVals: Posterior MCMC samples. Thus, for this example, each subject (66 total) has 4 chains with 4000 iterations, so with the 1000 burn in that leaves 3000 x 4 = 12000 samples per parameter. 

```{r}
#Subset individual parameters
bayes_ind <- bayes$allIndPars
bayes_ind <- bayes_ind %>%
  rename(id = subjID)

bayes_ind <- bayes_ind %>%
  separate(id, c("id", "vdate"))

#Get age and sex data.
merge_pet <- read.csv("merged_pet.csv", header = TRUE)
merge_pet %>% select(lunaid, vdate, behdatestr, dtbzdate)
merge_pet <- merge_pet %>% select(lunaid, 
                                  behdatestr, 
                                  age,
                                  sex) %>% rename(id = lunaid,
                                                  vdate = behdatestr)

#Trying to merge
merge_pet$id <- as.character(merge_pet$id) 
merge_pet$vdate <- as.character(merge_pet$vdate) 
#luna_7t <- left_join(bayes_ind, merge_pet, by = c("id", "vdate"))
pet_bayes <- merge(bayes_ind, merge_pet, by = c("id", "vdate"))
```

Imaging data

```{r}
#Get list of all txt files
temp_rest <- list.files(path = "C:/Users/djpet/Documents/daw_resting_state/corr_data", 
                        pattern = "mat",
                        full.names = TRUE)
temp_names <- list.files(path = "C:/Users/djpet/Documents/daw_resting_state/corr_data",
                         pattern = "mat")

#Read all txt files into list
datalist <- lapply(temp_rest,
                   FUN = read.table,
                   header = T)

#Creating row names
#dput(colnames(datalist[[1]]))
row_names <- dput(colnames(datalist[[1]]))

#Append row names to list elements
datalist <- lapply(datalist,
                   function(x) cbind(x, row_names))

#Creat wide dataframe for each element in list.
datalist <- lapply(1:length(datalist), 
                   function(x) (
                     pivot_wider(datalist[[x]], 
                                 names_from = row_names, 
                                 values_from = c("roi1","roi2", 
                                                 "roi3", "roi4", 
                                                 "roi5", "roi6", 
                                                 "roi7", "roi8",
                                                 "roi9", "roi10"))))

#Creat data frame that is 
rest_data <- bind_rows(datalist)
rest_data$tempid <- cbind(temp_names)


rest_data <- rest_data %>%
  separate(tempid, c("id", "vdate"))

# compute visit number
visit_info_rest <- rest_data %>% 
  select(id, vdate) %>% 
  group_by(id) %>% 
  distinct() %>% 
  mutate(visitnum=rank(as.numeric(as.character(vdate))))

#Merge visit number
rest_data <- merge(rest_data, 
             visit_info_rest %>% select(id, vdate, visitnum), 
             by=c('id','vdate'))

#Subsetting "upper-diagonal" values. No need for autocorrelation/diagonal in this case.
#Probably more elegant ways of doing this...

rest_data <- rest_data %>% 
  select(c("id", "vdate", "visitnum", 
           "roi1_roi2", "roi1_roi3", "roi1_roi4", "roi1_roi5", 
           "roi1_roi6", "roi1_roi7", "roi1_roi8", "roi1_roi9", 
           "roi1_roi10", 
           
           "roi2_roi3", "roi2_roi4", "roi2_roi5", "roi2_roi6", 
           "roi2_roi7", "roi2_roi8", "roi2_roi9", "roi2_roi10",  
           
           "roi3_roi4", "roi3_roi5", "roi3_roi6", 
           "roi3_roi7", "roi3_roi8", "roi3_roi9", "roi3_roi10",  
           
           "roi4_roi5", "roi4_roi6", "roi4_roi7", 
           "roi4_roi8", "roi4_roi9", "roi4_roi10", 
           
           "roi5_roi6", "roi5_roi7", "roi5_roi8", "roi5_roi9", 
           "roi5_roi10", 
           
           "roi6_roi7", "roi6_roi8", "roi6_roi9", "roi6_roi10",  
           
           "roi7_roi8", 
           "roi7_roi9", "roi7_roi10",  
           
           "roi8_roi9", 
           "roi8_roi10",  
           
           "roi9_roi10"))
#Looks correct
table(matrix(1:10,10,10) %>% upper.tri())

#Rename colums to ROI names.
#From Hera/Dan/scripts/README.txt (hint CTRL + SHIFT + C) huh?
#1. NAcc.nii.gz
#2. Putamen.nii.gz
#3. Caudate.nii.gz
#4. SMA 
#5. dlPFC 
#6. subgenualACC.nii.gz
#7. ventralACC.nii.gz
#8. rostralACC.nii.gz
#9. postmedofc.nii.gz (this might be OFC actually)
#10. anteriorvmPFC.nii.gz

rest_data <- rest_data %>% 
  rename(nacc_put = "roi1_roi2",
         nacc_ca = "roi1_roi3", 
         nacc_sma = "roi1_roi4",
         nacc_dlpfc = "roi1_roi5",
         nacc_sacc = "roi1_roi6",
         nacc_vacc = "roi1_roi7",
         nacc_racc = "roi1_roi8",
         nacc_pmofc = "roi1_roi9",
         nacc_avmpfc = "roi1_roi10",
         
         put_ca = "roi2_roi3",    
         put_sma = "roi2_roi4",
         put_dlpfc = "roi2_roi5",  
         put_sacc = "roi2_roi6",
         put_vacc = "roi2_roi7",
         put_racc = "roi2_roi8",
         put_pmofc = "roi2_roi9",
         put_avmpfc = "roi2_roi10",
         
         ca_sma = "roi3_roi4",   
         ca_dlpfc = "roi3_roi5",
         ca_sacc = "roi3_roi6",
         ca_vacc = "roi3_roi7", 
         ca_racc = "roi3_roi8",
         ca_pmofc = "roi3_roi9",
         ca_avmpfc = "roi3_roi10",
         
         sma_dlpfc = "roi4_roi5",   
         sma_sacc = "roi4_roi6",
         sma_vacc = "roi4_roi7",
         sma_racc = "roi4_roi8",
         sma_pmofc = "roi4_roi9",
         sma_avmpfc = "roi4_roi10",
         
         dlpfc_sacc = "roi5_roi6",
         dlpfc_vacc = "roi5_roi7",
         dlpfc_racc = "roi5_roi8",
         dlpfc_pmofc = "roi5_roi9",
         dlpfc_avmpfc = "roi5_roi10",
         
         sacc_vacc = "roi6_roi7",  
         sacc_racc = "roi6_roi8",
         sacc_pmofc = "roi6_roi9", 
         sacc_avmpfc = "roi6_roi10", 
           
         vacc_racc = "roi7_roi8", 
         vacc_pmofc = "roi7_roi9", 
         vacc_avpmc = "roi7_roi10",   
         
         racc_pmofc = "roi8_roi9",
         racc_avpmc = "roi8_roi10", 
         
         pmofc_avpmc = "roi9_roi10")


#Getting visit number for bet_bayes
#pet_bayes <- pet_bayes %>% 
#  select(id, vdate) %>% 
#  group_by(id) %>% 
#  distinct() %>% 
#  mutate(visitnum=rank(as.numeric(as.character(vdate))))
rest_data <- rest_data %>% filter(visitnum == 3 | 4)


pet_bayes <- merge(pet_bayes,
                rest_data,
                by = c("id")) %>% distinct()
dim(merge_test)
length(unique(merge_test$id))
```


Cool

```{r}
#This is PET, so only 1 time doing Daw task
ggplot(data = pet_bayes, 
       aes(x=nacc_dlpfc, y=beta)) + 
  geom_point() +
  #geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "gam",  aes(group = 1), color = "darkblue")

summary(lm(pi ~ 1 + age + sex, data = pet_bayes))
```

Pi (perseverance/persistance/sticky choice) parameter is in the expected direction (i.e., goes up with age).