---
title: "finn_tests"
author: "Daniel Petrie"
date: "2024-06-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

Goal of this script is to separate Daw task into 1st 100 trials vs last 100 trials. Could also be useful to break down further to get at changes in habit early vs. later.

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggeffects)
setwd("C:/Users/djpet/Documents/daw_resting_state")

#Beh DAW files /Volumes/Hera/Dan/daw/analysis/txt
luna_7t <- read.csv("cleaning/luna_7tbrainmech.csv", header = TRUE)
luna_pet <- read.csv("cleaning/luna_pet.csv", header = TRUE)

#File for ages
full <- read.csv("daw_project_060524.csv", header = TRUE)
```


Full cleaning.

```{r Full Cleaning}
#Creating a different sex variable for some plots/analyses
full <- full %>%
  mutate(sex = as.character(sex),
    sex_p = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female",
    TRUE ~ sex 
  ))

#Making visitnum a factor. Can change accordingly
full$visitnum <- as.factor(full$visitnum)

#Making sex a factor
full$sex <- as.factor(full$sex)

#Making an ordered factor.
full$sex_p <- ordered(full$sex_p, levels = (c("Male", "Female")))

#Inverse age for linear models.
full$inv_age <- 1/full$age

#Checking for duplicate rows due to weird merging situation I put myself in.
full[which(duplicated(full$modelbased)),c(1:3, 8, 20)] #11475_2/11498_2/11589_2 are duplicates.
#These ids have duplicated Daw visits, but different rest days. Taking rows with imaging data.

full <- full %>%
  filter(!(id == "11475" & visitnum == "2") & 
           !(id == "11498" & visitnum == "2") &
           !(id == "11589" & visitnum == "2"))

#Treating visitnum as numeric?
full$visitnum_numeric <- as.numeric(full$visitnum)
```


**Cleaning Daw Behavioral Data**

I am combining to run the logistic model. Then I will separate by study.

```{r Daw Cleaning}
#Separating id column into "id" and "visit"
luna_7t <- luna_7t %>%
  separate(id, c("id", "vdate"))

luna_pet <- luna_pet %>%
  separate(id, c("id", "vdate"))

#Adding trial number
luna_7t <- luna_7t %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

luna_pet <- luna_pet %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

#Removing id with identical data that was copied across studies.
luna_pet <- luna_pet %>% group_by(id) %>% filter(id != "11565")

#Removing ladder 200 trials from subject 11455. It is identical to first 200 trials and on the same day.
luna_pet <- luna_pet %>% filter(!(id == "11455" & trial > 200))

#Adding scanner information. Ashley slack stated that Siemens for 7T, Siemens Biograph mMR PET/MRI for PET. Seems like they only need a binary code situation here, but I will fuss with that during the neuroCombat portion of the code. This will also be useful for seeing which study came from what subje t.
luna_7t$study <- "7t"
luna_pet$study <- "PET"

#Similar id's across data sets. Check to make sure it looks correct with visit_info data set.
same_ids <- intersect(luna_7t$id, luna_pet$id)
same_ids
#"10195" ok
#"10997" ok
#"11537" ok
#"11561" ok
#"11565" Not ok. Tested on same day. Fixed above!
#"11575" ok
#"11641" ok
#"11651"
#luna_7t %>% filter(id == "11651")
#luna_pet %>% filter(id == "11651")
#visit_info %>% filter(id == "11651")

#Combining data. ADD HABIT HERE
luna_all <- bind_rows(luna_7t, luna_pet)

# compute visit number
luna_all <- luna_all %>% 
  group_by(id) %>% 
  mutate(visitnum = as.integer(factor(vdate, levels = unique(vdate))))

#Creating lagged variables. Add trial
luna_all <- luna_all %>% 
  group_by(id, visitnum) %>% 
  mutate(choice1lag = lag(choice1),
         choice2lag = lag(choice2),
         statelag = lag(state),
         moneylag = lag(money),
         visitnumlag = lag(visitnum))

# transitional vars...
luna_all <- luna_all %>% 
  mutate(commonrare = as.factor(ifelse((choice1lag == 1 & statelag == 2) |
                                         (choice1lag == 2 & statelag == 3),
                                       'common', 
                                       'rare')), 
         commonraredummy = ifelse(commonrare=="common", 
                                  1, 
                                  -1), 
         moneylagdummy = ifelse(moneylag == 1, 
                                1, 
                                -1), 
         firststagestay = ifelse(choice1 == choice1lag, 
                                 1, 
                                 0), 
         stayswitchwinlose = ifelse(firststagestay==1 & moneylag==0, 'lose-stay',
                             ifelse(firststagestay==1 & moneylag==1, 'win-stay', 
                                    ifelse(firststagestay==0 & moneylag==0,
                                           'lose-switch', 
                                           'win-switch'))))
luna_all <- luna_all %>% mutate(winswitch = ifelse(stayswitchwinlose== "win-switch",
                            1,
                            0))
luna_all <- luna_all %>% mutate(
  winswitch_common = ifelse(commonrare == "common" & 
                            stayswitchwinlose == "win-switch", 
                            1,
                            0),
  winswitch_rare = ifelse(commonrare == "rare" &
                            stayswitchwinlose == "win-switch",
                          1,
                          0))
```


Fitting the multilevel logistic regression model. I'll be using a "window" approach, where I will be fitting the model for the first 100 trials, and comparing to the last 100 trials. If nothing looks promising, I can pivot to bins of 50 trials.

```{r}
#Trials 1 - 50
intmodeltoplot_50 <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all %>% filter(trial <= 50),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_50) 

#Trials 51 - 100
intmodeltoplot_100 <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all %>% filter(trial > 50 & trial <= 100),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_100) 

#Trials 101 - 150
intmodeltoplot_150 <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all %>% filter(trial > 100 & trial <= 150),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_150) 

#Trials 151 - 200
intmodeltoplot_200 <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all %>% filter(trial > 150),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_200) 
```

At fixed effect level, estimates seem similar in magnitude. At random effects level, there seems to be some differences in variance estimates.

```{r}
#Extracting random effects
dawranefint_50 <- ranef(intmodeltoplot_50)
head(dawranefint_50$`id:visitnum`)

dawranefint_100 <- ranef(intmodeltoplot_100)
head(dawranefint_100$`id:visitnum`)

dawranefint_150 <- ranef(intmodeltoplot_150)
head(dawranefint_150$`id:visitnum`)

dawranefint_200 <- ranef(intmodeltoplot_200)
head(dawranefint_200$`id:visitnum`)

#Extracting fixed effects
dawfixedeffectsint_50 <- summary(intmodeltoplot_50)$coefficients
dawfixedeffectsint_50

dawfixedeffectsint_100 <- summary(intmodeltoplot_100)$coefficients
dawfixedeffectsint_100

dawfixedeffectsint_150 <- summary(intmodeltoplot_150)$coefficients
dawfixedeffectsint_150

dawfixedeffectsint_200 <- summary(intmodeltoplot_200)$coefficients
dawfixedeffectsint_200

#Creating dataframe consisting of MB/MF/Habit parameter for begining and end of task.
dawsubjecterms <- data.frame(
  idtemp = row.names(dawranefint_50$`id:visitnum`),
  #Trials 1-50
  modelbased_50 = dawranefint_50$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint_50[4,1], 
  modelfree_50 = dawranefint_50$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint_50[3,1],
  commonrare_50 = dawranefint_50$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint_50[2,1],
  firststagestay_50 = dawranefint_50$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint_50[1,1],
  #Trials 51-100
  modelbased_100 = dawranefint_100$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint_100[4,1], 
  modelfree_100 = dawranefint_100$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint_100[3,1],
  commonrare_100 = dawranefint_100$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint_100[2,1],
  firststagestay_100 = dawranefint_100$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint_100[1,1],
    #Trials 101-150
  modelbased_150 = dawranefint_150$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint_150[4,1], 
  modelfree_150 = dawranefint_150$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint_150[3,1],
  commonrare_150 = dawranefint_150$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint_150[2,1],
  firststagestay_150 = dawranefint_150$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint_150[1,1],
  #Trials 151-200
  modelbased_200 = dawranefint_200$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint_200[4,1], 
  modelfree_200 = dawranefint_200$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint_200[3,1],
  commonrare_200 = dawranefint_200$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint_200[2,1],
  firststagestay_200 = dawranefint_200$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint_200[1,1])
  
#Create id column
dawsubjecterms$id <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                            ":"),'[',1))
#Create visitnum column
dawsubjecterms$visitnum <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                                  ":"),'[',2))

#Zscoring Daw variables.
dawsubjecterms$modelbased_z_50 <- scale(dawsubjecterms$modelbased_50)
dawsubjecterms$modelbased_z_100 <- scale(dawsubjecterms$modelbased_100)
dawsubjecterms$modelbased_z_150 <- scale(dawsubjecterms$modelbased_150)
dawsubjecterms$modelbased_z_200 <- scale(dawsubjecterms$modelbased_200)
dawsubjecterms$modelfree_z_50 <- scale(dawsubjecterms$modelfree_50)
dawsubjecterms$modelfree_z_100 <- scale(dawsubjecterms$modelfree_100)
dawsubjecterms$modelfree_z_150 <- scale(dawsubjecterms$modelfree_150)
dawsubjecterms$modelfree_z_200 <- scale(dawsubjecterms$modelfree_200)
dawsubjecterms$firststagestay_z_50 <- scale(dawsubjecterms$firststagestay_50)
dawsubjecterms$firststagestay_z_100 <- scale(dawsubjecterms$firststagestay_100)
dawsubjecterms$firststagestay_z_150 <- scale(dawsubjecterms$firststagestay_150)
dawsubjecterms$firststagestay_z_200 <- scale(dawsubjecterms$firststagestay_200)
dawsubjecterms$commonrare_z_50 <- scale(dawsubjecterms$commonrare_50)
dawsubjecterms$commonrare_z_100 <- scale(dawsubjecterms$commonrare_100)
dawsubjecterms$commonrare_z_150 <- scale(dawsubjecterms$commonrare_150)
dawsubjecterms$commonrare_z_200 <- scale(dawsubjecterms$commonrare_200)

#Checking
head(dawsubjecterms)

# Selecting variable. Doing explicitly to reorder
dawsubjecterms <- dawsubjecterms %>% 
  dplyr::select(id, visitnum, 
               # "modelbased_50",  "modelfree_50",  "commonrare_50",  "firststagestay_50", 
               # "modelbased_100", "modelfree_100", "commonrare_100", "firststagestay_100", 
               # "modelbased_150", "modelfree_150", "commonrare_150", "firststagestay_150", 
               # "modelbased_200", "modelfree_200", "commonrare_200", "firststagestay_200",
                "modelbased_z_50",  "modelfree_z_50",  "commonrare_z_50",  "firststagestay_z_50", 
                "modelbased_z_100", "modelfree_z_100", "commonrare_z_100", "firststagestay_z_100", 
                "modelbased_z_150", "modelfree_z_150", "commonrare_z_150", "firststagestay_z_150", 
                "modelbased_z_200", "modelfree_z_200", "commonrare_z_200", "firststagestay_z_200") 


luna_sub <- luna_all %>% dplyr::select(id, visitnum, vdate, study) %>% distinct()


#Adding visit number number
#luna_all <- luna_all %>%
#  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
#  group_by(id) %>%
#  arrange(vdate) %>%
#  mutate(visitnum = dense_rank(vdate))

#Mergin date information with daw subject terms
dawsubjecterms <- merge(dawsubjecterms, luna_sub, by = c("id", "visitnum"))

#Rename visitnum after merging
dawsubjecterms <- dawsubjecterms %>% 
  #dplyr::select(!visitnum) %>% 
  #mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  rename(visitnum_daw = visitnum,
         behave.date = vdate) %>%
  mutate(behave.date = as.Date(behave.date, format = "%Y%m%d"))

#Creating 7t and PET data sep.
#daw_7t <- dawsubjecterms %>% filter(study == "7t")
#daw_pet <- dawsubjecterms %>% filter(study == "PET")
```

Combining ML-LR results with the daw parameters.

```{r Combining Data}
#Selecting columns of interest from full data set
full_sub <- full %>%
  dplyr::select(id, visitnum, age, study, sex, behave.date)

#Selecting columns of interest from Daw
#I think I will need firststagestay, moneylag, commonrate
#luna_all_sub <- luna_all %>%
#  dplyr::select(id, trial, visitnum, vdate, moneylag, moneylagdummy, commonrare, commonraredummy, firststagestay) %>%
#  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
#  rename(behave.date = vdate,
#         visitnum_daw = visitnum)
#
#Remember to organize by Date. Idea is to make sure that they match up appropriately.
stay_prob <- merge(dawsubjecterms, full_sub, by = c("id", "behave.date"))

#Adding dichotomous age
#stay_prob <- stay_prob %>%
#  mutate(age_cat = if_else(age < 18, 0, 1))
age_bins <- cut(stay_prob$age,
                breaks = c(10,13,17,24,34),
                labels = c("10_13", "14_17", "18-24", "25-34"),
                include.lowest = TRUE)
stay_prob <- stay_prob %>%
  mutate(age_cat = age_bins)

stay_prob$age_z <- scale(stay_prob$age)
```

Ok. Now I will look at trajectories according to whether it was the begining of the task vs. the end.

```{r}
mb_beg <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=modelbased_beg, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Based: Trials 1 - 100")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
mb_beg

mb_end <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=modelbased_end, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Based: Trials 100 - 200")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
mb_end
#Look slightly different.

mf_beg <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=modelfree_beg, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Free: Trials 1 - 100")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
mf_beg

mf_end <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=modelfree_end, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Free: Trials 101 - 200")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
mf_end


fss_beg <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=firststagestay_beg, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Free: Trials 1 - 100")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
fss_beg

fss_end <- lunaize(ggplot(data = stay_prob, 
               aes(x=age, y=firststagestay_end, group = id)) + 
  geom_point(size = 2, alpha = 0.7) +
  geom_line() +
  theme_bw() +
  #ylim(-3, 3) +
  stat_smooth(method = "gam",  aes(group = 1), color = "black", linewidth = 1.5) +
  #guides(fill = "none", color = "none") +
  labs(x = "Age", y = "RL Parameter Estimates", title = "Model Free: Trials 101 - 200")) +
  #scale_color_manual(values = c("blue", "red"), name = "Sex")) +
  theme(legend.position = "bottom") 
fss_end
```

It might be useful to make this data a bit longer for plotting and some statistical purposes.

```{r}
# Pivot longer
stay_prob_long <- stay_prob %>%
  pivot_longer(
    cols = starts_with("modelbased_z_") | starts_with("modelfree_z_") | starts_with("commonrare_z_") | starts_with("firststagestay_z_"),
    names_to = c(".value", "trial_set"),
    names_sep = "_z_"
  )

# Convert trial_set to a factor to ensure the correct order
stay_prob_long <- stay_prob_long %>%
  mutate(trial_set = factor(trial_set, levels = c("50", "100", "150", "200")))

# Pivot longer to create daw and value columns
stay_prob_longer <- stay_prob_long %>%
  pivot_longer(
    cols = c(modelbased, modelfree, commonrare, firststagestay),
    names_to = "daw",
    values_to = "value"
  )

stay_prob_longer <- stay_prob_longer %>%
  mutate(trial_set = factor(trial_set, levels = c("50", "100", "150", "200")))
```


Trying to see whether strategies are different at beginning vs end of task.

```{r}
#Descriptive statistics
stay_prob_long %>%
  group_by(age_cat, trial_set) %>%
  summarize(mean_fss = mean(firststagestay, na.rm = TRUE),
            sd_fss = sd(firststagestay, na.rm = TRUE))

ggplot(stay_prob_long, aes(x = trial_set, y = firststagestay, color = age_cat)) +
  geom_boxplot() +
  labs(title = "Behavioral Performance by Age and Trial Set")

model <- lmer(firststagestay ~ age * trial_set + (1|id), data = stay_prob_long)
summary(model)

ggplot(stay_prob_longer %>% filter(age_cat == "10_13" | age_cat == "14_17"), 
       aes(x = age, y = value, group = age_cat, colour = daw)) +
  geom_point() +
  geom_line()


#Line graph with everything.
stay_fss_summary <- stay_prob_longer %>% filter(daw == "firststagestay") %>%
  group_by(age_cat, trial_set) %>%
  summarize(mean_value = mean(value, na.rm = TRUE), .groups = 'drop')

ggplot(stay_fss_summary, aes(x = trial_set, y = mean_value, group = age_cat, color = age_cat)) +
  geom_line() +
  geom_point() +
  labs(title = "First Stage Stay Probability Across Trial Sets",
       x = "Trial Set",
       y = "Mean Value of FSS",
       color = "Age Category") +
  theme_minimal()

stay_mb_summary <- stay_prob_longer %>% filter(daw == "modelbased") %>%
  group_by(age_cat, trial_set) %>%
  summarize(mean_value = mean(value, na.rm = TRUE), .groups = 'drop')

ggplot(stay_mb_summary, aes(x = trial_set, y = mean_value, group = age_cat, color = age_cat)) +
  geom_line() +
  geom_point() +
  labs(title = "First Stage Stay Probability Across Trial Sets",
       x = "Trial Set",
       y = "Mean Value of MB",
       color = "Age Category") +
  theme_minimal()

stay_mf_summary <- stay_prob_longer %>% filter(daw == "modelfree") %>%
  group_by(age_cat, trial_set) %>%
  summarize(mean_value = mean(value, na.rm = TRUE), .groups = 'drop')

ggplot(stay_mf_summary, aes(x = trial_set, y = mean_value, group = age_cat, color = age_cat)) +
  geom_line() +
  geom_point() +
  labs(title = "First Stage Stay Probability Across Trial Sets",
       x = "Trial Set",
       y = "Mean Value of MB",
       color = "Age Category") +
  theme_minimal()


#Maybe looking at kids vs adults in sep plots with lines representing the different strategies?
# Calculate the mean value for each combination of trial_set and daw, filtered by age_cat
stay_prob_longer$value_z <- scale(stay_prob_longer$value)


stay_prob_summary_by_daw <- stay_prob_longer %>%
  filter(daw != "commonrare") %>%
  group_by(age_cat, trial_set, daw) %>%
  summarize(mean_value = mean(value_z, na.rm = TRUE), .groups = 'drop')

# Create the plot, faceting by age_cat
ggplot(stay_prob_summary_by_daw, aes(x = trial_set, y = mean_value, group = daw, color = daw)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ age_cat, nrow = 1) +
  labs(title = "Mean Values Across Trial Sets by DAW and Age Category",
       x = "Trial Set",
       y = "Mean Value",
       color = "DAW") +
  theme_minimal()

stay_prob_longer$trial_set_num <- as.numeric(stay_prob_longer$trial_set)
stay_prob_longer <- stay_prob_longer %>% filter(daw != "commonrare")

model <- lmer(value_z ~ age_cat * trial_set_num * daw + (1|id), data = stay_prob_longer)

summary(model)

p <- ggpredict(model, terms = c("trial_set_num", "daw", "age_cat"))
plot(p)
```

Extractin random effects

```{r}
model <- gam(value_z ~ 1 + s(age) + s(id, bs = "re"), method = "REML", data = stay_prob_longer)
```




Refitting ML LR. Keep in mind that Decker appears to extract MB/MF parameters with a model without age effects regressed out. This analyses is meant to supplement that and be used soley as behavioral analyses.

```{r Exploratory Models}

#NOTE: I can try and center trial, so 0 would reflect the middle of the task.
intmodeltoplot_t <- glmer(firststagestay ~ 1 + trial*age_z + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all,
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_t) #Damn...

intmodeltoplot_end <- glmer(firststagestay ~ 1 + age_z*commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=stay_prob %>% filter(trial > 101),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_end) #Damn...

#? Actually, this could be used on the full model I'd think.
#Model did not converge. But it doesn't not seem to 
intmodeltoplot_50 <- glmer(firststagestay ~ 1 + trial*age_z*commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=stay_prob %>% filter(trial < 51),
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot_50) #Damn...
```

Looking at some marginal effects. I think predicted probability of FSS over age would be the easiest place to start. I'd hope they are different. Then I could look at whether interactions look different.

```{r}
plot(predict_response(intmodeltoplot_50, terms = c("trial","age_z[-2,-1,0,1,2]")))
plot(predict_response(intmodeltoplot_50, terms = c("age_z", "moneylagdummy")))
```

Initial look seems that there is not much of a difference between beginning of session and end of session. I still need to extract effects and look a bit more critically tomorrow.