---
title: "hBayesDM"
author: "Daniel Petrie"
date: "2024-04-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

Libraries/wd()/data

```{r}
library("ggplot2") #For plotting
library("GGally") #ggpairs()
library("tidyverse") #Wranglin
library("dplyr") #Wranglin
library("interactions")
library("lme4") #MLM
library("lmerTest") #p-vals
library("ggeffects") #For marginal/conditional effects plots
library("margins") #For margins() function. Useful for comparing margins from ggeffects
library("marginaleffects") #For hypothesis_test()
library("parameters") #Other useful marginal effects functions
library("gdata") #upperTriangle()
library("mgcv") #GAMM
library("ggpubr") #Combining plots
library("bmlm") #Centering made easy
library("neuroCombat") #Harminization
library("LNCDR") #waterfall plot, lunaize plots 
library("gratia") #mgcv companion package. Using draw among other funcs.
#library("scales") #For Bart function
library("psych") #Descriptives
library("ggrain") #Raincloud plot
#library("corrplot") #Corrplot()
#Working directory (change to something better (onedrive?, something else?) at some point)
#Hera feels correct at this moment. All files could live in directory R for this project.
setwd("C:/Users/djpet/Documents/daw_resting_state")

#Beh DAW files /Volumes/Hera/Dan/daw/analysis/txt
luna_7t <- read.csv("luna_7tbrainmech.csv", header = TRUE)
luna_pet <- read.csv("luna_pet.csv", header = TRUE)

#Demographic files
#Location on hera. Note that I had to cp into /Hera/Dan/merged_files because of symbolic links.
#7t /Volumes/Hera/Projects/mMR_PETDA/scripts
#pet /Volumes/Hera/Projects/7TBrainMech/scripts
#Look into id's Maria sent...
#lunaid  alt.lunaid
#11390    11665
#11515    11748
merge_7t <- read.csv("merged_7t.csv", header = TRUE)
merge_pet <- read.csv("merged_pet.csv", header = TRUE)

#tat2 data
#/Volumes/Hera/Dan/tat2/out/smry
tat2_7t <- read.csv("atlas-harox_7t.csv", header = TRUE)
tat2_pet <- read.csv("atlas-harox_pet.csv", header =TRUE)

#hBayesdm data
par7 <- read.csv("par7_indpars.csv", header = TRUE)
```


**Cleaning Behavioral Data**


```{r}
#Separating id column into "id" and "visit"
luna_7t <- luna_7t %>%
  separate(id, c("id", "vdate"))

luna_pet <- luna_pet %>%
  separate(id, c("id", "vdate"))

#Adding trial number
luna_7t <- luna_7t %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

luna_pet <- luna_pet %>%
  group_by(id, vdate) %>%
  mutate(trial = row_number())

#Removing id with identical data that was copied across studies.
luna_pet <- luna_pet %>% group_by(id) %>% filter(id != "11565")

#Adding age to data sets. 
#Age related variable names
merge_7t %>% names %>% grep(value=T,pattern='age')
merge_7t %>% names %>% grep(value=T,pattern='date')
merge_pet %>% names %>% grep(value=T,pattern='age')
merge_pet %>% names %>% grep(value=T,pattern='vdate')
#I'll use sess.age for 7t. I think sess.age is average age at visit.
#I'll use age for pet. Not sure what others are getting at.
merge_7t <- merge_7t %>% dplyr::select(lunaid, 
                                behave.date, 
                                behave.age,
                                sex) %>% rename(id = lunaid,
                                                     age = behave.age,
                                                     vdate = behave.date)

merge_pet <- merge_pet %>% dplyr::select(lunaid, 
                                  behdatestr, 
                                  age,
                                  sex) %>% rename(id = lunaid,
                                                  vdate = behdatestr)

#Making id character variable for merging.
merge_7t$id <- as.character(merge_7t$id)
merge_7t$vdate <- as.character(merge_7t$vdate)
merge_pet$id <- as.character(merge_pet$id)
merge_pet$vdate <- as.character(merge_pet$vdate)

luna_7t <- left_join(luna_7t, merge_7t, by = c("id", "vdate"))
luna_pet <- merge(luna_pet, merge_pet, by = c("id", "vdate"))

#Adding scanner information. Ashley slack stated that Siemens for 7T, Siemens Biograph mMR PET/MRI for PET. Seems like they only need a binary code situation here, but I will fuss with that during the neuroCombat portion of the code. This will also be useful for seeing which study came from what subje t.
luna_7t$scanner <- "Siemens"
luna_pet$scanner <- "Biograph"

#Combining data. ADD HABIT HERE
luna_all <- bind_rows(luna_7t, luna_pet)

# compute visit number
visit_info <- luna_all %>% 
  dplyr::select(id, vdate) %>% 
  group_by(id) %>% 
  distinct() %>% 
  mutate(visitnum=rank(as.numeric(as.character(vdate))))

#Merge visit number
luna_all <- merge(luna_all, 
             visit_info %>% dplyr::select(id, vdate, visitnum), 
             by=c('id','vdate'))

#Similar id's across data sets. Check to make sure it looks correct with visit_info data set.
same_ids <- intersect(luna_7t$id, luna_pet$id)
same_ids
#"10195" ok
#"10997" ok
#"11537" ok
#"11561" ok
#"11565" Not ok. Tested on same day. Fixed above!
#"11575" ok
#"11641" ok
#"11651"
#luna_7t %>% filter(id == "11651")
#luna_pet %>% filter(id == "11651")
#visit_info %>% filter(id == "11651")

#Creating lagged variables. Add trial
luna_all <- luna_all %>% 
  group_by(id, visitnum) %>% 
  mutate(choice1lag = lag(choice1),
         choice2lag = lag(choice2),
         statelag = lag(state),
         moneylag = lag(money),
         visitnumlag = lag(visitnum))

# transitional vars...
luna_all <- luna_all %>% 
  mutate(commonrare = as.factor(ifelse((choice1lag == 1 & statelag == 2) |
                                         (choice1lag == 2 & statelag == 3),
                                       'common', 
                                       'rare')), 
         commonraredummy = ifelse(commonrare=="common", 
                                  1, 
                                  -1), 
         moneylagdummy = ifelse(moneylag == 1, 
                                1, 
                                -1), 
         firststagestay = ifelse(choice1 == choice1lag, 
                                 1, 
                                 0), 
         stayswitchwinlose = ifelse(firststagestay==1 & moneylag==0, 'lose-stay',
                             ifelse(firststagestay==1 & moneylag==1, 'win-stay', 
                                    ifelse(firststagestay==0 & moneylag==0,
                                           'lose-switch', 
                                           'win-switch'))))
luna_all <- luna_all %>% mutate(winswitch = ifelse(stayswitchwinlose== "win-switch",
                            1,
                            0))
luna_all <- luna_all %>% mutate(
  winswitch_common = ifelse(commonrare == "common" & 
                            stayswitchwinlose == "win-switch", 
                            1,
                            0),
  winswitch_rare = ifelse(commonrare == "rare" &
                            stayswitchwinlose == "win-switch",
                          1,
                          0))
```

Summary statistics behavioral

```{r}
luna_all %>% group_by(id, visitnum) %>% summarise(propstay=length(which(firststagestay==1))/n(),ntrials=n())

luna_all %>% group_by(id, visitnum) %>% summarise(propswitch=length(which(winswitch==1))/n(),ntrials=n())
```

Creating Daw variables involves a few steps.

Fit 2 glm models. One has MB/MF/first stage stay. Second has "winswitch" parameter. Eventually, these will all be merged into same data set with imaging time points.

1. Fit model
2. Extract fixed and random effects
3. Use fixed and random effects to create Daw scores.

```{r}
# models
intmodeltoplot <- glmer(firststagestay ~ 1 + commonraredummy*moneylagdummy + 
                          (commonraredummy*moneylagdummy|id:visitnum),
                        data=luna_all,
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplot)

# models
intmodeltoplotws <- glmer(winswitch ~ 1 + commonraredummy + 
                          (1 + commonraredummy|id:visitnum),
                        data=luna_all,
                        family="binomial",
                        glmerControl(optimizer = "bobyqa"))
summary(intmodeltoplotws)

#This model did not converge. Eigenvalue too large.
#intmodeltoplot_age <- glmer(firststagestay ~ 1 + age*commonraredummy*moneylagdummy +
#                          (commonraredummy*moneylagdummy|id:visitnum),
#                        data=luna_all,
#                        family="binomial",
#                        glmerControl(optimizer = "bobyqa"))
#summary(intmodeltoplot_age)

#Extracting random effects
dawranefint <- ranef(intmodeltoplot)
head(dawranefint$`id:visitnum`)

dawranefintws <- ranef(intmodeltoplotws)
head(dawranefintws$`id:visitnum`)

#Extracting fixed effects
dawfixedeffectsint <- summary(intmodeltoplot)$coefficients
dawfixedeffectsint

dawfixedeffectsintws <- summary(intmodeltoplotws)$coefficients
dawfixedeffectsintws

#Creating dataframe consisting of MB/MF/Habit parameter.
dawsubjecterms <- data.frame(
  idtemp = row.names(dawranefint$`id:visitnum`), 
  modelbased = dawranefint$`id:visitnum`$`commonraredummy:moneylagdummy` + 
    dawfixedeffectsint[4,1], 
  modelfree = dawranefint$`id:visitnum`$moneylagdummy + 
    dawfixedeffectsint[3,1],
  commonrare = dawranefint$`id:visitnum`$commonraredummy + 
    dawfixedeffectsint[2,1],
  firststagestay = dawranefint$`id:visitnum`$`(Intercept)` + 
    dawfixedeffectsint[1,1],
  winswitch = dawranefintws$`id:visitnum`$`(Intercept)` +
    dawfixedeffectsintws[1,1])
  

dawsubjecterms$id <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                            ":"),'[',1))

dawsubjecterms$visitnum <- unlist(lapply(strsplit(as.character(dawsubjecterms$idtemp),
                                                  ":"),'[',2))
#Checking
head(dawsubjecterms)

#Some cleaning for plotting
# age info
datereduce <- luna_all %>% dplyr::select(id, visitnum, age, sex, scanner) 
# merge with model terms
m <- merge(dawsubjecterms,datereduce,by=c('id','visitnum')) %>% distinct() #%>% filter(complete.cases(.))

#Z-scores just in case.
m <- m %>% mutate(
  modelfree_z = scale(modelfree),
  modelbased_z = scale(modelbased),
  commonrare_z = scale(commonrare),
  firststagestay_z = scale(firststagestay),
  winswitch_z = scale(winswitch),
  modeldiff_z = modelbased_z - modelfree_z
)
```

Ok. We now have a data set "m", that has ages and daw parameters at each visit. 

Cleaning rest data

7t: 292 imaging files

PET: 272 imaging files

NOTE: vmPFC list below.
25 Subgenual ACC (keep)
24 Ventral ACC (keep)
32 Rostral ACC (keep)
14c Posterior medial OFC (?, Ashley kept, but could delete.Keep)
#14r Rostral posterior medial OFC (remove)
#14rr (10?) anterior medial OFC (remove)
14m anterior vmPFC (keep)
#11m anterior medial OFC (remove)

```{r}
#Get list of all txt files
temp_rest <- list.files(path = "C:/Users/djpet/Documents/daw_resting_state/corr_data", 
                        pattern = "mat",
                        full.names = TRUE)
temp_names <- list.files(path = "C:/Users/djpet/Documents/daw_resting_state/corr_data",
                         pattern = "mat")

#Read all txt files into list
datalist <- lapply(temp_rest,
                   FUN = read.table,
                   header = T)

#Creating row names
#dput(colnames(datalist[[1]]))
row_names <- dput(colnames(datalist[[1]]))

#Append row names to list elements
datalist <- lapply(datalist,
                   function(x) cbind(x, row_names))

#Creat wide dataframe for each element in list.
datalist <- lapply(1:length(datalist), 
                   function(x) (
                     pivot_wider(datalist[[x]], 
                                 names_from = row_names, 
                                 values_from = c("roi1","roi2", 
                                                 "roi3", "roi4", 
                                                 "roi5", "roi6", 
                                                 "roi7", "roi8",
                                                 "roi9", "roi10"))))

#Creat data frame that is 
rest_data <- bind_rows(datalist)
rest_data$tempid <- cbind(temp_names)


rest_data <- rest_data %>%
  separate(tempid, c("id", "vdate"))

# compute visit number
visit_info_rest <- rest_data %>% 
  dplyr::select(id, vdate) %>% 
  group_by(id) %>% 
  distinct() %>% 
  mutate(visitnum=rank(as.numeric(as.character(vdate))))

#Merge visit number
rest_data <- merge(rest_data, 
             visit_info_rest %>% 
               dplyr::select(id, vdate, visitnum), 
             by=c('id','vdate'))

#Subsetting "upper-diagonal" values. No need for autocorrelation/diagonal in this case.
#Probably more elegant ways of doing this...

rest_data <- rest_data %>% 
  dplyr::select(c("id", "vdate", "visitnum", 
           "roi1_roi2", "roi1_roi3", "roi1_roi4", "roi1_roi5", 
           "roi1_roi6", "roi1_roi7", "roi1_roi8", "roi1_roi9", 
           "roi1_roi10", 
           
           "roi2_roi3", "roi2_roi4", "roi2_roi5", "roi2_roi6", 
           "roi2_roi7", "roi2_roi8", "roi2_roi9", "roi2_roi10",  
           
           "roi3_roi4", "roi3_roi5", "roi3_roi6", 
           "roi3_roi7", "roi3_roi8", "roi3_roi9", "roi3_roi10",  
           
           "roi4_roi5", "roi4_roi6", "roi4_roi7", 
           "roi4_roi8", "roi4_roi9", "roi4_roi10", 
           
           "roi5_roi6", "roi5_roi7", "roi5_roi8", "roi5_roi9", 
           "roi5_roi10", 
           
           "roi6_roi7", "roi6_roi8", "roi6_roi9", "roi6_roi10",  
           
           "roi7_roi8", 
           "roi7_roi9", "roi7_roi10",  
           
           "roi8_roi9", 
           "roi8_roi10",  
           
           "roi9_roi10"))
#Looks correct
table(matrix(1:10,10,10) %>% upper.tri())

#Rename colums to ROI names.
#From Hera/Dan/scripts/README.txt (hint CTRL + SHIFT + C) huh?
#1. NAcc.nii.gz
#2. Putamen.nii.gz
#3. Caudate.nii.gz
#4. SMA 
#5. dlPFC 
#6. subgenualACC.nii.gz
#7. ventralACC.nii.gz
#8. rostralACC.nii.gz
#9. postmedofc.nii.gz (this might be OFC actually)
#10. anteriorvmPFC.nii.gz

rest_data <- rest_data %>% 
  rename(nacc_put = "roi1_roi2",
         nacc_ca = "roi1_roi3", 
         nacc_sma = "roi1_roi4",
         nacc_dlpfc = "roi1_roi5",
         nacc_sacc = "roi1_roi6",
         nacc_vacc = "roi1_roi7",
         nacc_racc = "roi1_roi8",
         nacc_pmofc = "roi1_roi9",
         nacc_avmpfc = "roi1_roi10",
         
         put_ca = "roi2_roi3",    
         put_sma = "roi2_roi4",
         put_dlpfc = "roi2_roi5",  
         put_sacc = "roi2_roi6",
         put_vacc = "roi2_roi7",
         put_racc = "roi2_roi8",
         put_pmofc = "roi2_roi9",
         put_avmpfc = "roi2_roi10",
         
         ca_sma = "roi3_roi4",   
         ca_dlpfc = "roi3_roi5",
         ca_sacc = "roi3_roi6",
         ca_vacc = "roi3_roi7", 
         ca_racc = "roi3_roi8",
         ca_pmofc = "roi3_roi9",
         ca_avmpfc = "roi3_roi10",
         
         sma_dlpfc = "roi4_roi5",   
         sma_sacc = "roi4_roi6",
         sma_vacc = "roi4_roi7",
         sma_racc = "roi4_roi8",
         sma_pmofc = "roi4_roi9",
         sma_avmpfc = "roi4_roi10",
         
         dlpfc_sacc = "roi5_roi6",
         dlpfc_vacc = "roi5_roi7",
         dlpfc_racc = "roi5_roi8",
         dlpfc_pmofc = "roi5_roi9",
         dlpfc_avmpfc = "roi5_roi10",
         
         sacc_vacc = "roi6_roi7",  
         sacc_racc = "roi6_roi8",
         sacc_pmofc = "roi6_roi9", 
         sacc_avmpfc = "roi6_roi10", 
           
         vacc_racc = "roi7_roi8", 
         vacc_pmofc = "roi7_roi9", 
         vacc_avpmc = "roi7_roi10",   
         
         racc_pmofc = "roi8_roi9",
         racc_avpmc = "roi8_roi10", 
         
         pmofc_avpmc = "roi9_roi10")
```


**Cleaning time-averaged T2* (tat2) data**

```{r}
#Column for what study it is
tat2_7t <- tat2_7t %>%
  mutate(study = "tat2_7t")

tat2_pet <- tat2_pet %>%
  mutate(study = "tat2_pet")

#Combining studies
tat2_full <- rbind(tat2_7t, tat2_pet)

#Separating id column into "id" and "visit"
tat2_full <- tat2_full %>%
  separate(subj, c("id", "vdate"))

#Adding visit number number
tat2_full <- tat2_full %>%
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  group_by(id) %>%
  arrange(vdate) %>%
  mutate(visitnum = dense_rank(vdate))

#Removing obvious outlier 11487 visit 3
tat2_full <- tat2_full %>% 
  group_by(id) %>% 
  filter(input != "11487_20190516_tat2_novxscl_meant_medvol")
#Note. tat2_full is good for plotting distributions of tat2 variables in raincloud plot.


#Pivot wider (but still technically long data)
tat2_full_wider <- tat2_full %>%
  pivot_wider(id_cols = c(id, vdate, visitnum, study,),
              names_from = roi,
              values_from = beta)

rest_data <- merge(rest_data, 
             tat2_full_wider, 
             by=c('id','visitnum'))
```


**Cleaning hBayesDM data**


```{r}
#Separating id column into "id" and "visit"
par7 <- par7 %>%
  separate(subjID, c("id", "vdate"))

#Adding visit number number
par7 <- par7 %>%
  mutate(vdate = as.Date(vdate, format = "%Y%m%d")) %>%
  group_by(id) %>%
  arrange(vdate) %>%
  mutate(visitnum = dense_rank(vdate))

rest_data <- merge(rest_data, 
             par7, 
             by=c('id','visitnum'))
```


Merge in neuroimaging measures. Keeping code for all versions as sensitivity checks... merge seems to be the least amount of missing, and still 222 people (7t and pet) with 342 observations.

```{r}
merge_test <- merge(m,
                rest_data,
                by = c("id", "visitnum"))
dim(merge_test)
length(unique(merge_test$id))

rest_data$visitnum <- as.character(rest_data$visitnum)

left_join_test <- left_join(m,
                rest_data,
                by = c("id", "visitnum"))
dim(left_join_test)
length(unique(left_join_test$id))

full_join_test <- full_join(m,
                rest_data,
                by = c("id", "visitnum"))
dim(full_join_test)
length(unique(full_join_test$id))
```

For now, I will just use "merge_test". Probably worth doing sensitivity check across these data sets when I get the time.

```{r}
#Calling data "full"
full <- merge_test
#full <- full_join_test
```


**Neurocombat**


```{r}
temp_df <- full %>% 
  dplyr::select("id", "visitnum", "age", "sex", "study", "nacc_put", "nacc_ca", "nacc_sma", "nacc_dlpfc", 
"nacc_sacc", "nacc_vacc", "nacc_racc", "nacc_pmofc", "nacc_avmpfc", "put_ca", "put_sma", "put_dlpfc", "put_sacc", "put_vacc", 
"put_racc", "put_pmofc", "put_avmpfc", "ca_sma", 
"ca_dlpfc", "ca_sacc", "ca_vacc", "ca_racc", "ca_pmofc", "ca_avmpfc", "sma_dlpfc", "sma_sacc", "sma_vacc", "sma_racc", 
"sma_pmofc", "sma_avmpfc", "dlpfc_sacc", "dlpfc_vacc", 
"dlpfc_racc", "dlpfc_pmofc", "dlpfc_avmpfc", "sacc_vacc", 
"sacc_racc", "sacc_pmofc", "sacc_avmpfc", "vacc_racc", 
"vacc_pmofc", "vacc_avpmc", "racc_pmofc", "racc_avpmc", "pmofc_avpmc","harox_striatum", "harox_nacc", 
"harox_caudate", "harox_putamen", "harox_pallidum") %>% 
  drop_na("id", "visitnum", "age", "sex", "study", "nacc_put", "nacc_ca", "nacc_sma", "nacc_dlpfc", 
"nacc_sacc", "nacc_vacc", "nacc_racc", "nacc_pmofc", "nacc_avmpfc", "put_ca", "put_sma", "put_dlpfc", "put_sacc", "put_vacc", 
"put_racc", "put_pmofc", "put_avmpfc", "ca_sma", 
"ca_dlpfc", "ca_sacc", "ca_vacc", "ca_racc", "ca_pmofc", "ca_avmpfc", "sma_dlpfc", "sma_sacc", "sma_vacc", "sma_racc", 
"sma_pmofc", "sma_avmpfc", "dlpfc_sacc", "dlpfc_vacc", 
"dlpfc_racc", "dlpfc_pmofc", "dlpfc_avmpfc", "sacc_vacc", 
"sacc_racc", "sacc_pmofc", "sacc_avmpfc", "vacc_racc", 
"vacc_pmofc", "vacc_avpmc", "racc_pmofc", "racc_avpmc", "pmofc_avpmc","harox_striatum", "harox_nacc", 
"harox_caudate", "harox_putamen", "harox_pallidum") %>% 
  distinct()

##hypothetical combat

temp_df$sex <- gsub("M", "1", temp_df$sex)
temp_df$sex <- gsub("F", "2", temp_df$sex)

temp_df$study <- gsub("tat2_7t", "1", temp_df$study)
temp_df$study <- gsub("tat2_pet", "2", temp_df$study)


## actual combat 

batch <- as.factor(temp_df$study)
mod1 <- as.factor(temp_df$sex)
mod2 <- as.numeric(temp_df$age)
id <- as.factor(temp_df$id)

mod <- model.matrix(~mod2+mod1)

temp_df_combat <- temp_df %>% 
  dplyr::select(-id, -study, -sex, -age, -visitnum)

temp_df_combat_t <- temp_df_combat %>% t %>% as.matrix

data.harmonized <- neuroCombat(dat=temp_df_combat_t, batch=batch, mod=mod)

temp_df_combat_t_harmonized <- data.harmonized$dat.combat  

temp_df_combat_harmonized <- temp_df_combat_t_harmonized %>% t %>% as.data.frame

#Append suffix to all columns in harmonized data.
colnames(temp_df_combat_harmonized) <-
  paste(colnames(temp_df_combat_harmonized), "_harm", sep = "")

test <- cbind(temp_df, temp_df_combat_harmonized)

full <- full %>% dplyr::select("id", "visitnum", 
                        "modelbased", "modelfree", "commonrare",
                        "firststagestay", "winswitch", "modelfree_z", 
                        "modelbased_z", "commonrare_z", 
                        "firststagestay_z", "winswitch_z", 
                        "modeldiff_z","a1", "beta1", "a2", "beta2", "pi", "w", "lambda")


#full <- merge(full, test, by = c("id", "visitnum"))
full <- merge(full, test, by = c("id", "visitnum"), all = TRUE)
dim(full)
length(unique(full$id))
```

Making own data chunk for this to highlight importance. From my understanding, R2* = (1/T2*). So doing that here for analyses.

 In Larsen et al., (2020) he seems to be using R2* for all analyses. So I am doing that.
 
Note that after chatting with Will, it looks like inverse should be taken at voxel level using 3dcalc. Then averaged across the mask. The shape is still similar, but it is not 100% what Bart did. Discuss accordingly.
 

```{r}
#testing inverse tat2
full$harox_putamen_harm_inv <- 1/full$harox_putamen_harm
full$harox_nacc_harm_inv <- 1/full$harox_nacc_harm
full$harox_caudate_harm_inv <- 1/full$harox_caudate_harm
full$harox_pallidum_harm_inv <- 1/full$harox_pallidum_harm
```

Centering

```{r}
##PMC/GMC variables.
full <- isolate(full, by = "id", 
        value = c("modelbased", "modelfree", "commonrare", 
"firststagestay", "winswitch", "modelfree_z", "modelbased_z", 
"commonrare_z", "firststagestay_z", "winswitch_z", "modeldiff_z", 
"nacc_put_harm", "nacc_ca_harm", "nacc_sma_harm", "nacc_dlpfc_harm", 
"nacc_sacc_harm", "nacc_vacc_harm", "nacc_racc_harm", "nacc_pmofc_harm", "nacc_avmpfc_harm", "put_ca_harm", "put_sma_harm", "put_dlpfc_harm", 
"put_sacc_harm", "put_vacc_harm", "put_racc_harm", "put_pmofc_harm", 
"put_avmpfc_harm", "ca_sma_harm", "ca_dlpfc_harm", 
"ca_sacc_harm", "ca_vacc_harm", "ca_racc_harm", "ca_pmofc_harm", 
"ca_avmpfc_harm", "sma_dlpfc_harm", "sma_sacc_harm", 
"sma_vacc_harm", "sma_racc_harm", "sma_pmofc_harm", "sma_avmpfc_harm", "dlpfc_sacc_harm", "dlpfc_vacc_harm", "dlpfc_racc_harm", 
"dlpfc_pmofc_harm", "dlpfc_avmpfc_harm", 
"sacc_vacc_harm", "sacc_racc_harm", "sacc_pmofc_harm", "sacc_avmpfc_harm", "vacc_racc_harm", "vacc_pmofc_harm", "vacc_avpmc_harm", "racc_pmofc_harm", "racc_avpmc_harm", "pmofc_avpmc_harm", "harox_putamen_harm_inv", 
                          "harox_nacc_harm_inv",
                          "harox_caudate_harm_inv",
                          "harox_pallidum_harm_inv", "a1", "beta1", "a2", "beta2", "pi", "w", "lambda"), 
which = "both")
```

Ok now is giant data set.


First, I'll look at similarities between daw parameters either from the lagged analyses, or from hBayesDM

```{r}
#All RL parameters
ggpairs(full[,c("a1", "beta1", "a2", "beta2", "pi", "w", "lambda","modelbased", "modelfree", "commonrare", 
"firststagestay", "winswitch")])

#Habit parameters
full %>% ggplot(aes(x = firststagestay, y = pi)) +
  geom_point() +
  stat_smooth(method = "gam", color = "darkblue") +
  labs(x = "First Stage Stay", y = "Perseverance") +
  ggtitle("Bivariate Relations between FSS and pi")

#Goal-directed parameters
full %>% ggplot(aes(x = modelbased, y = w)) +
  geom_point() +
  stat_smooth(method = "gam", color = "darkblue") +
  labs(x = "Model Based", y = "Model-based Weight") +
  ggtitle("Bivariate Relations between FSS and pi")

#Comparing inverse temp
full %>% ggplot(aes(x = beta1, y = beta2)) +
  geom_point() +
  stat_smooth(method = "lm", color = "darkblue")# +
  #labs(x = "Model Based", y = "Model-based Weight") +
  #ggtitle("Bivariate Relations between FSS and pi")

#Comparing learning rates
full %>% ggplot(aes(x = a1, y = a2)) +
  geom_point() +
  stat_smooth(method = "lm", color = "darkblue")# +
  #labs(x = "Model Based", y = "Model-based Weight") +
  #ggtitle("Bivariate Relations between FSS and pi")

#ggplot(data = full %>% group_by(id) %>% filter(n() > 1), 
#       aes(x=age, y=harox_putamen_harm_inv_cw, group = id)) + 
#  geom_point() +
#  geom_line() +
#  theme_bw(base_size = 15) +
#  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
#  ggtitle("Within-Person R2* Putamen") 
```

Looking at trends over age.

```{r}
#Learning rate
ggplot(data = full, 
       aes(x=age, y=a1_cb, group = id)) + 
  geom_point() +
  #geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") #+
  #ggtitle("Within-Person R2* Putamen") 

#Learning rate
ggplot(data = full, 
       aes(x=age, y=a2_cb, group = id)) + 
  geom_point() +
  #geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") #+
  #ggtitle("Within-Person R2* Putamen") 

#Inv Temp
ggplot(data = full, 
       aes(x=age, y=beta1, group = id)) + 
  geom_point() +
  geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
  ggtitle("Within-Person R2* Putamen") 

#Inv Temp
ggplot(data = full, 
       aes(x=age, y=beta2, group = id)) + 
  geom_point() +
  geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
  ggtitle("Within-Person R2* Putamen") 

#perseverance
ggplot(data = full, 
       aes(x=age, y=pi, group = id)) + 
  geom_point() +
  geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
  ggtitle("Within-Person R2* Putamen") 

#mbw
ggplot(data = full, 
       aes(x=age, y=w_cb, group = id)) + 
  geom_point() +
  geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
  ggtitle("Within-Person R2* Putamen") 

#Lambda
ggplot(data = full, 
       aes(x=age, y=lambda, group = id)) + 
  geom_point() +
  geom_line() +
  theme_bw(base_size = 15) +
  stat_smooth(method = "lm",  aes(group = 1), color = "darkblue") +
  ggtitle("Within-Person R2* Putamen") 

#FC and RL
full %>% ggplot(aes(x = put_sma_harm, y = pi)) +
  geom_point() +
  stat_smooth(method = "gam", color = "darkblue") +
  #labs(x = "Model Based", y = "Model-based Weight") +
  ggtitle("Bivariate Relations between FSS and pi")

#DA and RL
full %>% ggplot(aes(x = harox_pallidum_harm_inv, y = w)) +
  geom_point() +
  stat_smooth(method = "gam", color = "darkblue")

#"put_ca_harm", "put_sma_harm", "put_dlpfc_harm", 
#"put_sacc_harm", "put_vacc_harm", "put_racc_harm", "put_pmofc_harm", 
#"put_avmpfc_harm"


t <- gamm(pi ~ 1 + sex + visitnum +
            s(age, k = 3, fx = TRUE) +
            s(put_avmpfc_harm_cb, k = 3, fx = TRUE) 
            +s(harox_putamen_harm_inv_cb, k = 3, fx = TRUE)
          , 
               random = list(id = ~1), 
                       method = "REML", 
                       data = full)
summary(t$gam)
draw(t$gam)
#lunaize(plot(ggpredict(t$gam,
#               terms = c(" harox_putamen_harm_inv",
#                         "age"))))
```

```{r}
ggpairs(full[,c("a1", "beta1", "a2", "beta2", "pi", "w", "lambda",
                "harox_putamen_harm_inv_cb",
                "put_sma_harm_cb", 
                "put_dlpfc_harm_cb",
                "put_sacc_harm_cb",        
                "put_vacc_harm_cb",
                "put_racc_harm_cb",         
                "put_pmofc_harm_cb",       
                "put_avmpfc_harm_cb")])
```

Ok. It appears that there are some relations between FC and the RL parameters. Worth looking at 

```{r}
#Treating visitnum as numeric?
full$visitnum <- as.numeric(full$visitnum)
#a path, indirect effect
m2 <- lm(harox_putamen_harm_inv_cb ~ 1 + sex + visitnum +
            pi_cb, 
          #method = "REML", 
          data = full %>% filter(complete.cases(.)))
summary(m2)

m3 <- lm(put_sma_harm_cb ~ 1 + sex + visitnum + pi_cb +
            harox_putamen_harm_inv_cb, 
            #harox_putamen_harm_inv,
          #method = "REML", 
          data = full %>% filter(complete.cases(.)))
summary(m3)

#Note that visitnum messes things up. Perhaps change to factor/numeric?
#Testing moderated mediation models. Looking at "high habit" people.
#high_habit <- mean(full$firststagestay_z) - sd(full$firststagestay_z)

testing <- mediation::mediate(m2, m3, 
                              treat = "pi_cb",
                   mediator = "harox_putamen_harm_inv_cb", 
                   boot = T, 
                   sims = 100)
summary(testing)
plot(testing)
```

avmPFC worked at between-person level.
?sma?